---
title: "FreeSurfer_ADNI"
author: "nforde"
date: "December 11, 2018"
output: html_document
---
# get libraries/set paths
```{r get libraries & set paths}
library(tidyverse)
library(broom)
library(knitr)
library(car)
library(cowplot)
library(lme4)
library(ggbrain)
library(gridExtra)
library(reshape2)

## set all the paths
#ADNI

library(ADNIMERGE)
demog <- filter(adnimerge, VISCODE == "bl" | VISCODE =="sc", DX.bl == "CN", AGE >= 65, AGE <=85)
FS_orig <- filter(ucsffsx, VISCODE == "sc")
FSdict <- read.csv("/scratch/nforde/ADNI/UCSFFSLX44_DICT_11_01_13.csv")

outdir <- "/projects/nforde/HCP/stats/ADNI"

```
# define functions

```{r define functions}
## for normalising data
transform_to_normal <- function(X) {
  # calculate the best exponent using powerTransform:
  pT <- powerTransform(X)
  # apply the power transform and save the result to a new variable
  X_pT <- X^pT$lambda ## note ^ is exponent in r
  return(X_pT)
}

## function to extract stats from lm
extract <- function(X,num){ 
  lapply(X, function(i){
    F_age <- lapply(get(i), function(f) Anova(f)$"F value"[1])
    F_sex <- lapply(get(i), function(f) Anova(f)$"F value"[2])
    F_XTBVheight <-lapply(get(i), function(f) Anova(f)$"F value"[3])
    p_age <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[1])
    p_sex <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[2])
    p_XTBVheight <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[3])
    adjRsq <- sapply(get(i), function(f) summary(f)$adj.r.squared)
    padj_age <- p.adjust(p_age, method="fdr", n=num)
    padj_sex <- p.adjust(p_sex, method="fdr", n=num)
    padj_XTBVheight <- p.adjust(p_XTBVheight, method="fdr", n=num)
    
    merged <- as.data.frame(cbind(F_age, padj_age, F_sex, padj_sex, F_XTBVheight, padj_XTBVheight, adjRsq))
    return(merged)
  })
}

## function to extract stats from lmer
extract_lmer <- function(i){ 
  Chi_age <- lapply((i), function(f) Anova(f)$"Chisq"[1])
  Chi_sex <- lapply((i), function(f) Anova(f)$"Chisq"[2])
  Chi_hemi <-lapply((i), function(f) Anova(f)$"Chisq"[3])
  Chi_sexXhemi <-lapply((i), function(f) Anova(f)$"Chisq"[4])
  p_age <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[1])
  p_sex <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[2])
  p_hemi <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[3])
  p_sexXhemi <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[4])
  padj_age <- p.adjust(p_age, method="fdr")
  padj_sex <- p.adjust(p_sex, method="fdr")
  padj_hemi <- p.adjust(p_hemi, method="fdr")
  padj_sexXhemi <- p.adjust(p_sexXhemi, method="fdr")
    
  merged <- as.data.frame(cbind(Chi_age, padj_age, Chi_sex, padj_sex, Chi_hemi, padj_hemi, Chi_sexXhemi, padj_sexXhemi))
  return(merged)
}

extractT <- function(i, num){
  Tval <- lapply((i), function(f) f$statistic)
  Pval <- lapply((i), function(f) f$p.value)
  dof <- lapply((i), function(f) f$parameter)
   
  Padj <- p.adjust(Pval, method="fdr", n=num)
  Cohen <- (as.numeric(Tval)*2)/sqrt(as.numeric(dof))
  
  merged <- as.data.frame(cbind(Tval, Padj, Cohen))
  return(merged)

}

## function to extract stats from var.test
extract_var <- function(X, num){ 
  VR <- lapply(X, function(f) (f)$"estimate")
  VR_p <- lapply(X, function(f) (f)$"p.value")
  padj_VR <- p.adjust(VR_p, method="fdr", n=num)
  
  merged <- as.data.frame(cbind(VR, padj_VR))
  return(merged)
}


### function to plot and grid multiple figures
plot_box <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Sex, color= Sex)) + geom_boxplot(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none"))
  # grid <- do.call(grid.arrange, a)
  return(a)
} #

#same as above, split violin instead of box
plot_vio <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x="Sex", fill= Sex)) + geom_split_violin(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text.y=element_text(size=8),
                      axis.title=element_text(size=10), legend.position="none")
              +stat_summary(aes_string(y=f), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", shape =95, 
                            size=0.5, position = position_dodge(width = .75)))
  return(a)
} #
# 
# +stat_summary(aes_string(y="Caudate"), fun.y=mean, geom="point", shape=23, size=2, position = position_dodge(width = .75))

# +stat_summary(aes_string(y="Caudate"), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", size=1, position = position_dodge(width = .75))


plot_age <- function(ROIs,df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Age, color =Sex)) +xlab("Age (years)") 
              + theme(axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none") 
              + geom_jitter(aes_string(y=f), width=0.2, size= 0.5) + geom_smooth(aes_string(y=f), span = 0.5))
  return(a)
}

### function to plot measure by sex, grouped by hemisphere
plot_box_hemi <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=hemi, fill = Sex)) + geom_boxplot(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none"))
  return(a)
} #

#same as above, split violin instead of box
plot_vio_hemi <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=hemi, fill = Sex)) + geom_split_violin(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none") 
              +stat_summary(aes_string(y=f), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", shape =95, size=0.5, 
                            position = position_dodge(width = .75)))
  return(a)
} #

# + scale_x_discrete(labels= c("Female","Male"))  + theme(axis.title.x = element_blank())
# plot X by age and gender
plot_age_hemi <- function(ROIs,df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Age, color =Sex)) +xlab("Age (years)") 
              + geom_jitter(aes_string(y=f), width=0.2, size= 0.5) + geom_smooth(aes_string(y=f), span = 0.5) 
              + facet_grid(. ~hemi , scales = "free_y")
              + theme(axis.text=element_text(size=10), axis.title=element_text(size=12), legend.position="none", 
                      strip.text = element_text(size=12)))
  return(a)
}

#+ xlab("Age (years)") + scale_shape_manual(values=c(4,1)) #change shapes,  scale_linetype_manual(values=c("dotdash", "dotted")) # Change linetypes
#legend.position="none", , strip.background = element_rect(size= 3)

# a<-  + geom_boxplot(outlier.shape = NA, lwd=0.3)
# b <- scale_x_discrete(labels= c("HmarrangeGrobC","ADHD","TS"))
# c <- a +b   + theme(legend.text=element_text(size=4), axis.title.x = element_blank(), axis.title.y = element_text(size=5), axis.text.x=element_text(size=4, colour="black"), axis.text.y = element_text(size=4, colour="black"),plot.title=element_text(size=6)) + ylab("FA") +guides(fill=FALSE) +scale_fill_manual(values=c("grey","white"))+ ylim(0.2,0.45)              
# grid <- theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank())
# ggsave(file="C:/Users/p270073/Dropbox/work/data/Compuls/dMRI/graph.pdf",g, width=8, height=10, dpi=300)
# save_plot

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1,'group']
  newdata <- plyr::arrange(transform(data, x = if(grp%%2==1) xminv else xmaxv), if(grp%%2==1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1,nrow(newdata)-1,nrow(newdata)), 'x'] <- round(newdata[1, 'x']) 
  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 
                                              1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, position = position, show.legend = show.legend, inherit.aes = inherit.aes, params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}

```
# organise
```{r organise data}
FS_qcd <- filter(FS_orig, OVERALLQC == "Pass") %>% distinct(RID, .keep_all = TRUE)

#Need to fo FS renaming!
FS <- FS_qcd[c(2, 21:366)] %>% 
   gather(ROI, metric, starts_with("ST")) %>%
   merge(FSdict, by.x="ROI", by.y = "ROIcode") %>%
  select("RID", "ROIname", "metric") %>% 
  spread(key = ROIname, value = metric)
FS <- select(FS, - contains("CorpusCallosum"), - contains("Unknown"))

# select subset of demogs of interest
demog$Sex <- demog$PTGENDER
demog$Age <- demog$AGE
demogs <- demog[c("RID", "Sex", "Age")]

# calc total wm and gm vol
FS$Vol_Total_GM <- (FS$L_Vol_CerebralCortex + FS$R_Vol_CerebralCortex)
FS$Vol_Tot_WM <- (FS$L_Vol_CerebralWM + FS$R_Vol_CerebralWM) 
FS$Vol_Cerebellum_Cort <- (FS$L_Vol_CerebellumCortex + FS$R_Vol_CerebellumCortex)
FS$Vol_Cerebellum_WM <- (FS$L_Vol_CerebellumWM + FS$R_Vol_CerebellumWM) 
FS$Vol_BrainSeg_No_Vent <- (FS$Vol_Total_GM + FS$Vol_Tot_WM + FS$Vol_Cerebellum_Cort + FS$Vol_Cerebellum_WM)

# Isolate vol measures and separate out hemis  
Vol.df <- FS %>% select(contains("Vol")) %>% cbind(FS[c("RID")]) 
colnames(Vol.df) <- sub("Vol_", "", colnames(Vol.df)) 

Vol.R <- Vol.df %>% select(starts_with("R_")) %>% cbind(Vol.df[c("RID", "BrainSeg_No_Vent")]) 
colnames(Vol.R) <- sub("R_", "", colnames(Vol.R)) 
Vol.R$hemi <- "right" 

Vol.L <- Vol.df %>% select(starts_with("L_")) %>% cbind(Vol.df[c("RID", "BrainSeg_No_Vent")]) 
colnames(Vol.L) <- sub("L_", "", colnames(Vol.L)) 
Vol.L$hemi <- "left" 

Vol.hemi <- rbind(Vol.R, Vol.L)

Vol.df <- merge(Vol.df, demogs, by=("RID"))
Vol.hemi <- merge(Vol.hemi, demogs, by=("RID"))

## Cortical thickness
CT.df <- FS %>% select(contains("CT_")) %>% cbind(FS[c("RID")]) 
colnames(CT.df) <- sub("CT_", "", colnames(CT.df)) 

CT.R <- CT.df %>% select(starts_with("R_")) %>% cbind(CT.df[c("RID")])
colnames(CT.R) <- sub("R_", "", colnames(CT.R)) 
CT.R$hemi <- "right" 

CT.L <- CT.df %>% select(starts_with("L_")) %>% cbind(CT.df[c("RID")])
colnames(CT.L) <- sub("L_", "", colnames(CT.L)) 
CT.L$hemi <- "left" 

CT.hemi <- rbind(CT.R, CT.L)

CT.df <- merge(CT.df, demogs, by=("RID")) %>% merge(Vol.df[c("RID", "BrainSeg_No_Vent")], by=("RID"))  
CT.hemi <- merge(CT.hemi, demogs, by=("RID")) %>% merge(Vol.df[c("RID", "BrainSeg_No_Vent")], by=("RID"))  


### Surface Area
SA.df <- FS %>% select(contains("SA_")) %>% cbind(FS[c("RID")])
colnames(SA.df) <- sub("SA_", "", colnames(SA.df)) 

SA.R <- SA.df %>% select(starts_with("R_")) %>% cbind(SA.df[c("RID")])
colnames(SA.R) <- sub("R_", "", colnames(SA.R)) 
SA.R$hemi <- "right" 

SA.L <- SA.df %>% select(starts_with("L_")) %>% cbind(SA.df[c("RID")])
colnames(SA.L) <- sub("L_", "", colnames(SA.L)) 
SA.L$hemi <- "left" 

SA.hemi <- rbind(SA.L, SA.R)

SA.df <- merge(SA.df, demogs, by=("RID")) %>% merge(Vol.df[c("RID", "BrainSeg_No_Vent")], by=("RID"))  
SA.hemi <- merge(SA.hemi, demogs, by=("RID")) %>% merge(Vol.df[c("RID", "BrainSeg_No_Vent")], by=("RID"))  



### lists of variables
overall <- c("Total_GM", "Tot_WM", "Cerebellum_Cort", "Cerebellum_WM") 
overallincTBV <- c("BrainSeg_No_Vent", "Total_GM", "Tot_WM", "Cerebellum_Cort", "Cerebellum_WM") 
SubCortLR <- c("L_Thalamus", "L_Caudate", "L_Putamen", "L_Pallidum", "L_Hippocampus", "L_Amygdala", "L_AccumbensArea", "R_Thalamus", "R_Caudate", "R_Putamen",  "R_Pallidum", "R_Hippocampus",  "R_Amygdala", "R_AccumbensArea")
SubCort <- c("Thalamus", "Caudate", "Putamen", "Pallidum", "Hippocampus", "Amygdala", "AccumbensArea")

CortLR <- names(CT.df)[2:69]
Cort <- names(CT.hemi)[2:35]
```
# Stats Overall
```{r mean stats global}
### Total Brain Volume (BrainSeg_No_Vent) analysisH
TBVsimpX <- lm(BrainSeg_No_Vent ~ Age*Sex, data=Vol.df)
TBVsimp <- lm(BrainSeg_No_Vent ~ Age + Sex, data=Vol.df)
TBVageres <- lm(BrainSeg_No_Vent ~ Age, data=Vol.df)
TBVageres1 <- augment(TBVageres)
TBVageres.df <- cbind(Vol.df, TBVageres1)
TBVage <- t.test(.resid ~ Sex, data=TBVageres.df)

TBVmods <- list(TBVsimpX, TBVsimp)

## TBV extract measures
F_age <- lapply(TBVmods, function(f) Anova(f)$"F value"[1])
F_sex <- lapply(TBVmods, function(f) Anova(f)$"F value"[2])
F_Xheight <-lapply(TBVmods, function(f) Anova(f)$"F value"[3])
p_age <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[1])
p_sex <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[2])
p_Xheight <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[3])
adjRsq <- sapply(TBVmods, function(f) summary(f)$adj.r.squared)
padj_age <- p.adjust(p_age, method="fdr", n=5) ############
padj_sex <- p.adjust(p_sex, method="fdr", n=5) ############
padj_Xheight <- p.adjust(p_Xheight, method="fdr", n=5) ############

TBVt <- TBVage$statistic
TBVp <- TBVage$p.value
TBVdof <- TBVage$parameter
TBVpadj <- p.adjust(TBVp, method="fdr", n=5) ############
TBVCohen <- (as.numeric(TBVt)*2)/sqrt(as.numeric(TBVdof))

TBV_out <- as.data.frame(cbind(F_age, padj_age, F_sex, padj_sex, F_Xheight, padj_Xheight, adjRsq, TBVt, TBVpadj, TBVCohen))
TBV_out <- apply(TBV_out,2,as.character)
TBVout.file <- paste(outdir, "TBV.csv", sep="/")
write.csv(TBV_out, file=TBVout.file, row.names = F)

###### total GM and total WM 

## overall simple with interactions
overall_simpX  <- lapply(overall, function(i){
  lm(get(i) ~ Age*Sex, data=Vol.df)
})
## overall simple
overall_simp  <- lapply(overall, function(i){
  lm(get(i) ~ Age +Sex, data=Vol.df)
})

### make df including residuals from TBV and height mods
# Vol.res <- subset(Vol.df, ! is.na(Height))
Vol.res <- Vol.df

OVres_age  <- lapply(overall, function(i){
  lm(get(i) ~ Age, data=Vol.res)
})
OVres_TBV  <- lapply(overall, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=Vol.res)
})
OVres_full  <- lapply(overall, function(i){
  lm(get(i) ~ BrainSeg_No_Vent +Age, data=Vol.res)
})

for (i in 1:length(overall)) {
  res <- augment(OVres_age[[i]])
  names(res) <- paste0(overall[i],"age",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[5]))
}
for (i in 1:length(overall)) {
  res <- augment(OVres_TBV[[i]])
  names(res) <- paste0(overall[i],"TBV",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[5]))
}
for (i in 1:length(overall)) {
  res <- augment(OVres_full[[i]])
  names(res) <- paste0(overall[i],"Full",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[6]))
}

OVres_age_ls <-Vol.res %>% select(contains("age.resid")) %>% names
OVres_TBV_ls <-Vol.res %>% select(contains("TBV.resid")) %>% names
OVres_full_ls <-Vol.res %>% select(contains("Full.resid")) %>% names

overall_age  <- lapply(OVres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=Vol.res)
})
overall_TBV  <- lapply(OVres_TBV_ls, function(i){
  lm(get(i) ~ Age + Sex , data=Vol.res)
})
overall_TBVX  <- lapply(OVres_TBV_ls, function(i){
  lm(get(i) ~ Age*Sex , data=Vol.res)
})
overall_full  <- lapply(OVres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=Vol.res)
})

OVmodels <- c("overall_simpX", "overall_simp", "overall_TBV", "overall_TBVX")

overall_out <- extract(OVmodels, 5) ################
OV_simpX <- overall_out[[1]]
OV_simp <- overall_out[[2]]
OV_TBV <- overall_out[[3]]
OV_TBVX <- overall_out[[4]]

names(OV_simpX) <- paste0('simpX_',names(OV_simpX))
names(OV_simp) <- paste0('simp_',names(OV_simp))
names(OV_TBV) <- paste0('TBV_',names(OV_TBV))
names(OV_TBVX) <- paste0('TBVX_',names(OV_TBVX))

OVresid_age <- extractT(overall_age, 5) ############
names(OVresid_age) <- paste0('AgeResid',names(OVresid_age))
OVresid_full <- extractT(overall_full, 5) ############
names(OVresid_full) <- paste0('FullResid',names(OVresid_full))

### merge and write out
OV_out <- cbind(OV_simpX, OV_simp, OV_TBV, OV_TBVX, OVresid_age, OVresid_full)
OV_out <- apply(OV_out,2,as.character)
rownames(OV_out) <- overall
OVout.file <- paste(outdir, "overall.csv", sep="/")
write.csv(OV_out, file=OVout.file, row.names = T)

```
# Overall variance testing
```{r VR stats global}
# raw model
Vol.M <- subset(Vol.res, Sex == "Male")
Vol.F <- subset(Vol.res, Sex == "Female")

TBVageres.M <- subset(TBVageres.df, Sex == "Male")
TBVageres.F <- subset(TBVageres.df, Sex == "Female")

# for TBV only
TBV_var <- var.test(Vol.M$BrainSeg_No_Vent, Vol.F$BrainSeg_No_Vent)
TBV_est <- TBV_var$estimate
TBV_VRp <- TBV_var$p.value
TBV_VRpadj <- p.adjust(TBV_VRp, method="fdr", n=5) ######

TBVres_var <- var.test(TBVageres.M$BrainSeg_No_Vent, TBVageres.F$BrainSeg_No_Vent)
TBVres_est <- TBVres_var$estimate
TBVres_VRp <- TBVres_var$p.value
TBVres_VRpadj <- p.adjust(TBV_VRp, method="fdr", n=5) ###########

TBV_VR <- cbind(TBV_est, TBV_VRpadj,TBVres_est, TBVres_VRpadj) 
OVoutTBV_VR.file <- paste(outdir, "TBV_VR.csv", sep="/")
write.csv(TBV_VR, file=OVoutTBV_VR.file, row.names = T)

# for the rest of the overall measures
overall_var  <- lapply(overall, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar <- extract_var(overall_var, 5)###########

# residual mods
overall_var.resAge  <- lapply(OVres_age_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resAge <- extract_var(overall_var.resAge, 5)###########

overall_var.resTBV  <- lapply(OVres_TBV_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resTBV <- extract_var(overall_var.resTBV, 5)###########

overall_var.resfull  <- lapply(OVres_full_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resfull <- extract_var(overall_var.resfull, 5)###########

# write out
names(OVvar) <- paste0('VR_',names(OVvar))
names(OVvar.resAge) <- paste0('VR_Age_',names(OVvar.resAge))
names(OVvar.resTBV) <- paste0('VR_TBV_',names(OVvar.resTBV))
names(OVvar.resfull) <- paste0('VR_Full_',names(OVvar.resfull))

OV_VR <- cbind(OVvar, OVvar.resAge, OVvar.resTBV, OVvar.resfull)
OV_VR <- apply(OV_VR,2,as.character)
rownames(OV_VR) <- overall
OVoutVR.file <- paste(outdir, "overallVR.csv", sep="/")
write.csv(OV_VR, file=OVoutVR.file, row.names = T)

```
# Overall Plots raw (for age plots) and minus age (box and vio)
```{r plots global}
OVplots_age <- plot_age(overallincTBV, Vol.df)

OV_to_graph_age <- c("BrainSeg_No_Vent", "Total_GMage.resid", "Tot_WMage.resid", "Cerebellum_Cortage.resid", "Cerebellum_WMage.resid") #########
OVplots_box <- plot_box(OV_to_graph_age, Vol.res)
OVplots_vio <- plot_vio(OV_to_graph_age, Vol.res) 

plot_grid(plotlist=OVplots_age, align="hv", ncol = 3)  
plot_grid(plotlist=OVplots_box, align="hv", ncol = 3)
plot_grid(plotlist=OVplots_vio, align="hv", ncol = 3)

OV2 <- plot_grid(plotlist=OVplots_age, align="hv", ncol = 3)  
OV1 <- plot_grid(plotlist=OVplots_box, align="hv", ncol = 3)
OV3 <- plot_grid(plotlist=OVplots_vio, align="hv", ncol = 3)

OVfile.box <- paste(outdir, "OVgraphBox.png", sep="/")
OVfile.age <- paste(outdir, "OVgraphAge.png", sep="/")
OVfile.vio <- paste(outdir, "OVgraphVio.png", sep="/")

ggsave(OVfile.box, OV1, dpi=300, width = 21, height = 14, units = "cm") #####
ggsave(OVfile.age, OV2, dpi=300, width = 21, height = 14, units = "cm") #####
ggsave(OVfile.vio, OV3, dpi=300, width = 21, height = 14, units = "cm") #####

```
# Overall Plots - minus TBV (age plots), minus age and TBV (vio)
```{r plots global without TBV}

OV_to_graph_TBV <- c("BrainSeg_No_Vent", OVres_TBV_ls) 
OV_to_graph_full <- c("BrainSeg_No_Vent", OVres_full_ls) 

OVplots_age.res <- plot_age(OV_to_graph_TBV, Vol.res)
OVplots_vio.res <- plot_vio(OV_to_graph_full, Vol.res)

plot_grid(plotlist=OVplots_age.res, align="hv", ncol = 3)
plot_grid(plotlist=OVplots_vio.res, align="hv", ncol = 3)

OV2.res <- plot_grid(plotlist=OVplots_age.res, align="hv", ncol =3)
OV3.res <- plot_grid(plotlist=OVplots_vio.res, align="hv", ncol =3)

OVfile.age.res <- paste(outdir, "OVgraphAgeRES.png", sep="/")
OVfile.vio.res <- paste(outdir, "OVgraphVioRES.png", sep="/")

ggsave(OVfile.age.res, OV2.res, dpi=300, width = 21, height = 14, units = "cm") ######
ggsave(OVfile.vio.res, OV3.res, dpi=300, width = 21, height = 14, units = "cm") #########

#alt config
AltOV1 <- plot_grid((OVplots_vio[[1]] + ylab("Total Brain Volume")), (OVplots_vio[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_vio[[3]]+ ylab("Cerebral White Matter")), (OVplots_vio[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_vio[[5]]+ ylab("Cerebellar White Matter")), NULL ,(OVplots_vio.res[[2]]+ ylab("Cerebral Grey Matter")),  
                    (OVplots_vio.res[[3]]+ ylab("Cerebral White Matter")), (OVplots_vio.res[[4]]+ ylab("Cerebellar Grey Matter")),  
                    (OVplots_vio.res[[5]]+ ylab("Cerebellar White Matter")), align="hv", ncol =5, 
                    labels=c('A', 'B', 'C', 'D', 'E', ' ', 'F', 'G', 'H', 'I', 'J'), label_size=10)
AltOV2 <- plot_grid((OVplots_age[[1]]+ ylab("Total Brain Volume")), (OVplots_age[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_age[[3]]+ ylab("Cerebral White Matter")), (OVplots_age[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_age[[5]]+ ylab("Cerebellar White Matter")), NULL, (OVplots_age.res[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_age.res[[3]]+ ylab("Cerebral White Matter")), (OVplots_age.res[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_age.res[[5]]+ ylab("Cerebellar White Matter")), align="hv", ncol =5, 
                    labels=c('A', 'B', 'C', 'D', 'E', ' ', 'F', 'G', 'H', 'I', 'J'), label_size=10)

OVfile.alt1 <- paste(outdir, "OVgraphVio_comb.png", sep="/")
OVfile.alt2 <- paste(outdir, "OVgraphAge_comb.png", sep="/")

ggsave(OVfile.alt1, AltOV1, dpi=300, width = 21, height = 8, units = "cm")
ggsave(OVfile.alt2, AltOV2, dpi=300, width = 30, height = 12, units = "cm")

```
# top/bottom subs OV
```{r top and bottom quantiles}
# ##Q1 is smallest Q20 largest
# #OV_to_graph_full list to use
# 
# OV_Qs <- mutate_at(Vol.res, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# OV_QsM <- mutate_at(Vol.M, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# OV_QsF <- mutate_at(Vol.F, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# OV_Qs <- OV_Qs %>% select(ends_with("_Q")) %>% cbind(OV_Qs[1]) 
# OV_QsM <- OV_QsM %>% select(ends_with("_Q")) %>% cbind(OV_QsM[1]) 
# OV_QsF <- OV_QsF %>% select(ends_with("_Q")) %>% cbind(OV_QsF[1]) 

```
# sub cortical stats mean 
```{r mean stats subcortical}
## Stats sub cort

## SubCort simple with interactions
subCort_simpX  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age*Sex, data=Vol.df)
})

## SubCort simple
subCort_simp  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age +Sex, data=Vol.df)
})

### make df including residuals from TBV 
SC.res <- Vol.df
SCres_age  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age, data=SC.res)
})
SCres_TBV  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=SC.res)
})
SCres_Full  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age, data=SC.res)
})

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_age[[i]])
  names(res) <- paste0(SubCortLR[i],"age",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[5]))
}

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_TBV[[i]])
  names(res) <- paste0(SubCortLR[i],"TBV",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[5]))
}

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_Full[[i]])
  names(res) <- paste0(SubCortLR[i],"Full",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[6]))
}

SCres_age_ls <-SC.res %>% select(contains("age.resid")) %>% names
SCres_TBV_ls <-SC.res %>% select(contains("TBV.resid")) %>% names
SCres_full_ls <-SC.res %>% select(contains("Full.resid")) %>% names

subCort_age  <- lapply(SCres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=SC.res)
})
subCort_TBV  <- lapply(SCres_TBV_ls, function(i){
  lm(get(i) ~ Age + Sex , data=SC.res)
})
subCort_TBVX  <- lapply(SCres_TBV_ls, function(i){
  lm(get(i) ~ Age*Sex , data=SC.res)
})
subCort_full  <- lapply(SCres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=SC.res)
})

## SubCort hemi
subCort_hemi  <- lapply(SubCort, function(i){
  lmer(get(i) ~ Age + Sex*hemi + (1|RID), data=Vol.hemi)
})

SCmodels <- c("subCort_simpX", "subCort_simp", "subCort_TBV", "subCort_TBVX")

numSC=length(SubCortLR) #set how many corrections
subcort_out <- extract(SCmodels, numSC)
SC_simpX <- subcort_out[[1]]
SC_simp <- subcort_out[[2]]
SC_TBV <- subcort_out[[3]]
SC_TBVX <- subcort_out[[4]]
SC_hemi <- extract_lmer(subCort_hemi) 

names(SC_simpX) <- paste0('simpX_',names(SC_simpX))
names(SC_simp) <- paste0('simp_',names(SC_simp))
names(SC_TBV) <- paste0('TBV_',names(SC_TBV))
names(SC_TBVX) <- paste0('TBVX_',names(SC_TBVX))
names(SC_hemi) <- paste0('hemi_',names(SC_hemi)) 

SCresid_age <- extractT(subCort_age, numSC)
names(SCresid_age) <- paste0('AgeResid_',names(SCresid_age))
SCresid_full <- extractT(subCort_full, numSC)
names(SCresid_full) <- paste0('FullResid_',names(SCresid_full))

## merge and write out
SC_out <- cbind(SC_simpX, SC_simp, SC_TBV, SC_TBVX, SCresid_age, SCresid_full, SC_hemi) 
SC_out <- apply(SC_out,2,as.character)
rownames(SC_out) <- SubCortLR
SCout.file <- paste(outdir, "SC.csv", sep="/")
write.csv(SC_out, file=SCout.file, row.names = T)

```
# Subcortical variance testing
```{r VR stats subcortical}
# raw model
# Vol.M <- subset(SC.res, Sex == "Male")
# Vol.F <- subset(SC.res, Sex == "Female")

SC.M.res <- subset(SC.res, Sex == "Male") ##SC.res made above includes residuals 
SC.F.res <- subset(SC.res, Sex == "Female")

SubCort_var  <- lapply(SubCortLR, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar <- extract_var(SubCort_var, numSC)

SubCort_var.resAge  <- lapply(SCres_age_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resAge <- extract_var(SubCort_var.resAge, numSC)

SubCort_var.resTBV  <- lapply(SCres_TBV_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resTBV <- extract_var(SubCort_var.resTBV, numSC)

SubCort_var.resfull  <- lapply(SCres_full_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resfull <- extract_var(SubCort_var.resfull, numSC)

# write out
names(SCvar) <- paste0('VR_',names(SCvar))
names(SCvar.resAge) <- paste0('VR_Age_',names(SCvar.resAge))
names(SCvar.resTBV) <- paste0('VR_TBV_',names(SCvar.resTBV))
names(SCvar.resfull) <- paste0('VR_Full_',names(SCvar.resfull))

SC_VR <- cbind(SCvar, SCvar.resAge, SCvar.resTBV, SCvar.resfull)
SC_VR <- apply(SC_VR,2,as.character)
rownames(SC_VR) <- SubCortLR
SCoutVR.file <- paste(outdir, "SC_VR.csv", sep="/")
write.csv(SC_VR, file=SCoutVR.file, row.names = T)

```

# Subcortical Plots - raw (for age plots) and minus age (box and vio)
```{r plots subcortical}
# make df with hemi and residual data
SC.R.res <- SC.res %>% select(starts_with("R_")) %>% cbind(SC.res[1])
colnames(SC.R.res) <- sub("R_", "", colnames(SC.R.res)) 
SC.R.res$hemi <- "right" 

SC.L.res <- SC.res %>% select(starts_with("L_")) %>% cbind(SC.res[1])
colnames(SC.L.res) <- sub("L_", "", colnames(SC.L.res)) 
SC.L.res$hemi <- "left" 

SC.hemi.res <- rbind(SC.R.res, SC.L.res)
SC.hemi.res <- merge(SC.hemi.res, demogs, by=("RID")) 

#make lists of regions based on residuals
SC_to_graph_full <-SC.hemi.res %>% select(contains("Full.resid")) %>% names
SC_to_graph_TBV <-SC.hemi.res %>% select(contains("TBV.resid")) %>% names
SC_to_graph_age <-SC.hemi.res %>% select(contains("age.resid")) %>% names

#plot 
SCplots_age <- plot_age_hemi(SubCort, Vol.hemi)
SCplots_box <- plot_box_hemi(SC_to_graph_age, SC.hemi.res)
SCplots_vio <- plot_vio_hemi(SC_to_graph_age, SC.hemi.res)

# check what they look like
plot_grid(plotlist=SCplots_box, align="hv", ncol =3)
plot_grid(plotlist=SCplots_age, align="hv", ncol =2)
plot_grid(plotlist=SCplots_vio, align="hv", ncol =3)

# set arrangement
SC1 <- plot_grid(plotlist=SCplots_box, align="hv", ncol =3)
SC2 <- plot_grid(plotlist=SCplots_age, align="hv", ncol =2)
SC3 <- plot_grid(plotlist=SCplots_vio, align="hv", ncol =3)

#set file names
SCfile.box <- paste(outdir, "SCgraphBox.png", sep="/")
SCfile.age <- paste(outdir, "SCgraphAge.png", sep="/")
SCfile.vio <- paste(outdir, "SCgraphVio.png", sep="/")

#save graphs
ggsave(SCfile.box, SC1, dpi=300, width = 21, height = 17.82, units = "cm")
ggsave(SCfile.age, SC2, dpi=300, width = 21, height = 24, units = "cm")
ggsave(SCfile.vio, SC3, dpi=300, width = 21, height = 17.82, units = "cm")

```
# Subcortical Plots - minus TBV (age plots), minus age and TBV (vio)
```{r plots subcortical without TBV}
#plot 
SCplots_age.res <- plot_age_hemi(SC_to_graph_TBV, SC.hemi.res)
SCplots_vio.res <- plot_vio_hemi(SC_to_graph_full, SC.hemi.res)

#check config
plot_grid(plotlist=SCplots_age.res, align="hv", ncol = 3)
plot_grid(plotlist=SCplots_vio.res, align="hv", ncol = 3)

#set config
SC2.res <- plot_grid(plotlist=SCplots_age.res, align="hv", ncol =2)
SC3.res <- plot_grid(plotlist=SCplots_vio.res, align="hv", ncol =3)

#set file names
SCfile.age.res <- paste(outdir, "SCgraphAgeRES.png", sep="/")
SCfile.vio.res <- paste(outdir, "SCgraphVioRES.png", sep="/")

#save
ggsave(SCfile.age.res, SC2.res, dpi=300, width = 21, height = 24, units = "cm")
ggsave(SCfile.vio.res, SC3.res, dpi=300, width = 21, height = 17.82, units = "cm")


#alt config combining with and without TBV
AltSC1 <- plot_grid((SCplots_vio[[1]] + ylab("Thalamus")), (SCplots_vio.res[[1]]+ ylab("Thalamus")), 
                    (SCplots_vio[[2]] +ylab("Caudate")), (SCplots_vio.res[[2]] +ylab("Caudate")), 
                    (SCplots_vio[[3]] +ylab("Putamen")), (SCplots_vio.res[[3]] +ylab("Putamen")),
                    (SCplots_vio[[4]] +ylab("Pallidum")), (SCplots_vio.res[[4]] +ylab("Pallidum")),
                    (SCplots_vio[[5]] +ylab("Hippocampus")), (SCplots_vio.res[[5]] +ylab("Hippocampus")),
                    (SCplots_vio[[6]] +ylab("Amygdala")), (SCplots_vio.res[[6]] +ylab("Amygdala")),
                    (SCplots_vio[[7]] +ylab("Nucleus Accumbens")), (SCplots_vio.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =2)

AltSC3 <- plot_grid((SCplots_vio[[1]] + ylab("Thalamus")),  (SCplots_vio[[2]] +ylab("Caudate")),
                     (SCplots_vio[[3]] +ylab("Putamen")),  (SCplots_vio[[4]] +ylab("Pallidum")),
                    (SCplots_vio[[5]] +ylab("Hippocampus")),(SCplots_vio[[6]] +ylab("Amygdala")), 
                    (SCplots_vio[[7]] +ylab("Nucleus Accumbens")),(SCplots_vio.res[[1]]+ ylab("Thalamus")), 
                    (SCplots_vio.res[[2]] +ylab("Caudate")), (SCplots_vio.res[[3]] +ylab("Putamen")),
                    (SCplots_vio.res[[4]] +ylab("Pallidum")), (SCplots_vio.res[[5]] +ylab("Hippocampus")),
                    (SCplots_vio.res[[6]] +ylab("Amygdala")), (SCplots_vio.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =7)


AltSC2 <- plot_grid((SCplots_age[[1]] +ylab("Thalamus")), (SCplots_age.res[[1]] + ylab("Thalamus")),
                    (SCplots_age[[2]] +ylab("Caudate")), (SCplots_age.res[[2]] +ylab("Caudate")), 
                    (SCplots_age[[3]] +ylab("Putamen")), (SCplots_age.res[[3]] +ylab("Putamen")),
                    (SCplots_age[[4]] +ylab("Pallidum")), (SCplots_age.res[[4]] +ylab("Pallidum")), 
                    (SCplots_age[[5]] +ylab("Hippocampus")), (SCplots_age.res[[5]] +ylab("Hippocampus")), 
                    (SCplots_age[[6]] +ylab("Amygdala")), (SCplots_age.res[[6]] +ylab("Amygdala")),
                    (SCplots_age[[7]] +ylab("Nucleus Accumbens")), (SCplots_age.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =2)

SCfile.alt1 <- paste(outdir, "SCgraphVio_comb.png", sep="/")
SCfile.alt2 <- paste(outdir, "SCgraphAge_comb.png", sep="/")
SCfile.alt3 <- paste(outdir, "SCgraphVio_comb2.png", sep="/")

ggsave(SCfile.alt1, AltSC1, dpi=300, width = 16, height = 29.7, units = "cm")
ggsave(SCfile.alt2, AltSC2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SCfile.alt3, AltSC3, dpi=300, width = 29.7, height = 8, units = "cm")

### just to get a legend
# leg <- ggplot(Vol.hemi.res, aes(x= hemi, fill = Sex, y= ThalamusProperFull.resid)) + geom_split_violin() 
# leg.file <- paste(outdir, "legend.png", sep="/") 
# ggsave(leg.file, leg, dpi=300, width = 16, height = 16, units = "cm")

```
# top/bottom subs SC
```{r top and bottom quantiles SC}
##Q1 is smallest Q20 largest
#SCres_full_ls list to use

# SC_Qs <- mutate_at(SC.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SC_QsM <- mutate_at(SC.M.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SC_QsF <- mutate_at(SC.F.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# SC_Qs <- SC_Qs %>% select(ends_with("_Q")) %>% cbind(SC_Qs[1]) 
# SC_QsM <- SC_QsM %>% select(ends_with("_Q")) %>% cbind(SC_QsM[1]) 
# SC_QsF <- SC_QsF %>% select(ends_with("_Q")) %>% cbind(SC_QsF[1]) 
# 

```

# subcortical atlas plot 
```{r Atlas plot SC}
# SCtoplot <- as.data.frame(SC_VR)
# SCtoplot$hemi <- c("left","left", "left","left", "left","left", "left","right", "right","right","right","right","right","right")
# SCtoplot$area <- c("Thalamus Proper", "Caudate", "Putamen", "Pallidum", "Hippocampus", "Amygdala", "Accumbens", "Thalamus Proper", "Caudate", "Putamen",  "Pallidum", "Hippocampus",  "Amygdala", "Accumbens")
# 
# SCtoplot_sig <- subset(SCtoplot, as.numeric(levels(VR_padj_VR)) < 0.05)
# 
# ggbrain(SCtoplot_sig, atlas="aseg", mapping=aes(fill=VR_VR), colour="black", size=1)  #### this isn't correct, should be left and right hemis and numeric
# 
# 

```
# stats cortical CT means
```{r mean stats CT}

## CT simple with interactions
CortCT_simpX  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age*Sex, data=CT.df)
})

## Cort simple
CortCT_simp  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age +Sex, data=CT.df)
})

### make df including residuals from TBV 
CT.res <- CT.df
CTres_age  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age, data=CT.res)
})
CTres_TBV  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=CT.res)
})
CTres_Full  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age, data=CT.res)
})

for (i in 1:length(CortLR)) {
  res <- augment(CTres_age[[i]])
  names(res) <- paste0(CortLR[i],"age",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(CTres_TBV[[i]])
  names(res) <- paste0(CortLR[i],"TBV",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(CTres_Full[[i]])
  names(res) <- paste0(CortLR[i],"Full",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[6]))
}

CTres_age_ls <-CT.res %>% select(contains("age.resid")) %>% names
CTres_TBV_ls <-CT.res %>% select(contains("TBV.resid")) %>% names
CTres_full_ls <-CT.res %>% select(contains("Full.resid")) %>% names

CT_age  <- lapply(CTres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=CT.res)
})
CortCT_TBV  <- lapply(CTres_TBV_ls, function(i){
  lm(get(i) ~ Age + Sex , data=CT.res)
})
CortCT_TBVX  <- lapply(CTres_TBV_ls, function(i){
  lm(get(i) ~ Age*Sex , data=CT.res)
})
CT_full  <- lapply(CTres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=CT.res)
})

## CT hemi
CortCT_hemi  <- lapply(Cort, function(i){
  lmer(get(i) ~ Age + Sex*hemi + (1|RID), data=CT.hemi)
})

CTmodels <- c("CortCT_simpX", "CortCT_simp", "CortCT_TBV", "CortCT_TBVX")

numCT=length(CortLR) #set how many corrections
CT_out <- extract(CTmodels, numCT)
CT_simpX <- CT_out[[1]]
CT_simp <- CT_out[[2]]
CT_TBV <- CT_out[[3]]
CT_TBVX <- CT_out[[4]]
CT_hemi <- extract_lmer(CortCT_hemi) 

names(CT_simpX) <- paste0('simpX_',names(CT_simpX))
names(CT_simp) <- paste0('simp_',names(CT_simp))
names(CT_TBV) <- paste0('TBV_',names(CT_TBV))
names(CT_TBVX) <- paste0('TBVX_',names(CT_TBVX))
names(CT_hemi) <- paste0('hemi_',names(CT_hemi)) 

CTresid_age <- extractT(CT_age, numCT)
names(CTresid_age) <- paste0('AgeResid_',names(CTresid_age))
CTresid_full <- extractT(CT_full, numCT)
names(CTresid_full) <- paste0('FullResid_',names(CTresid_full))

## merge and write out
CT_out_tbl <- cbind(CT_simpX, CT_simp, CT_TBV, CT_TBVX, CTresid_age, CTresid_full, CT_hemi) 
CT_out_tbl <- apply(CT_out_tbl,2,as.character)
rownames(CT_out_tbl) <- CortLR
CTout.file <- paste(outdir, "CT.csv", sep="/")
write.csv(CT_out_tbl, file=CTout.file, row.names = T)

```
#  stats cortical CT variance
```{r VR stats CT}
CT.M <- subset(CT.df, Sex == "Male") # 
CT.F <- subset(CT.df, Sex == "Female")

CTCort_var  <- lapply(CortLR, function(i){
  var.test(CT.M[[i]], CT.F[[i]])
})
CTvar <- extract_var(CTCort_var, numCT)

CT.M.res <- subset(CT.res, Sex == "Male") # 
CT.F.res <- subset(CT.res, Sex == "Female")

CTCort_var.resAge  <- lapply(CTres_age_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resAge <- extract_var(CTCort_var.resAge, numCT)

CTCort_var.resTBV  <- lapply(CTres_TBV_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resTBV <- extract_var(CTCort_var.resTBV, numCT)

CTCort_var.resfull  <- lapply(CTres_full_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resfull <- extract_var(CTCort_var.resfull, numCT)

# write out
names(CTvar) <- paste0('VR_',names(CTvar))
names(CTvar.resAge) <- paste0('VR_Age_',names(CTvar.resAge))
names(CTvar.resTBV) <- paste0('VR_TBV_',names(CTvar.resTBV))
names(CTvar.resfull) <- paste0('VR_Full_',names(CTvar.resfull))

CT_VR <- cbind(CTvar, CTvar.resAge, CTvar.resTBV, CTvar.resfull)
CT_VR <- apply(CT_VR,2,as.character)
rownames(CT_VR) <- CortLR
CToutVR.file <- paste(outdir, "CT_VR.csv", sep="/")
write.csv(CT_VR, file=CToutVR.file, row.names = T)

```
# plot CT - raw (for age plots) and minus age (box and vio)
```{r plots CT}
#mk df with hemis and resid data
CT.R.res <- CT.res %>% select(starts_with("R_")) %>% cbind(CT.res[1])
colnames(CT.R.res) <- sub("R_", "", colnames(CT.R.res)) 
CT.R.res$hemi <- "right" 

CT.L.res <- CT.res %>% select(starts_with("L_")) %>% cbind(CT.res[1])
colnames(CT.L.res) <- sub("L_", "", colnames(CT.L.res)) 
CT.L.res$hemi <- "left" 

CT.hemi.res <- rbind(CT.R.res, CT.L.res)
CT.hemi.res <- merge(CT.hemi.res, demogs, by=("RID")) 

#make lists of regions based on residuals
CT_to_graph_age <-CT.hemi.res %>% dplyr::select(contains("age.resid")) %>% names
CT_to_graph_TBV <-CT.hemi.res %>% dplyr::select(contains("TBV.resid")) %>% names
CT_to_graph_full <-CT.hemi.res %>% dplyr::select(contains("Full.resid")) %>% names

#plot
CTplots_box <- plot_box_hemi(CT_to_graph_age, CT.hemi.res)
CTplots_age <- plot_age_hemi(Cort, CT.hemi)
CTplots_vio <- plot_vio_hemi(CT_to_graph_age, CT.hemi.res)

#check arrangement
marrangeGrob(grobs=CTplots_box, ncol =3, nrow =3)
marrangeGrob(grobs=CTplots_age, ncol =2, nrow =2)
marrangeGrob(grobs=CTplots_vio, ncol =3, nrow =3)

#set arranglement
CT1 <- marrangeGrob(grobs=CTplots_box, ncol =3, nrow =5)
CT2 <- marrangeGrob(grobs=CTplots_age, ncol =2, nrow =4)
CT3 <- marrangeGrob(grobs=CTplots_vio, ncol =3, nrow =5)

#set file names
CTfile.box <- paste(outdir, "CTgraphBox.pdf", sep="/")
CTfile.age <- paste(outdir, "CTgraphAge.pdf", sep="/")
CTfile.vio <- paste(outdir, "CTgraphVio.pdf", sep="/")

#save
ggsave(CTfile.box, CT1, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.age, CT2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.vio, CT3, dpi=300, width = 21, height = 29.7, units = "cm")

```
# CT Plots - minus TBV (age plots), minus age and TBV (vio)
```{r plots CT without TBV}
#plot
CTplots_age.res <- plot_age_hemi(CT_to_graph_TBV, CT.hemi.res)
CTplots_vio.res <- plot_vio_hemi(CT_to_graph_full, CT.hemi.res)

#check arrangment
marrangeGrob(grobs=CTplots_age.res, ncol = 2, nrow =2)
marrangeGrob(grobs=CTplots_vio.res, ncol = 3, nrow =3)

#set arrangment
CT2.res <- marrangeGrob(grobs=CTplots_age.res, ncol =2, nrow =4)
CT3.res <- marrangeGrob(grobs=CTplots_vio.res, ncol =3, nrow =5)

#set file names
CTfile.age.res <- paste(outdir, "CTgraphAgeRES.pdf", sep="/")
CTfile.vio.res <- paste(outdir, "CTgraphVioRES.pdf", sep="/")

#save
ggsave(CTfile.age.res, CT2.res, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.vio.res, CT3.res, dpi=300, width = 21, height = 29.7, units = "cm")

```

# top/bottom subs CT
```{r top & bottom quantiles CT}
##Q1 is smallest Q20 largest
#CTres_full_ls list to use

# CT_Qs <- mutate_at(CT.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# CT_QsM <- mutate_at(CT.M.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# CT_QsF <- mutate_at(CT.F.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# CT_Qs <- CT_Qs %>% select(ends_with("_Q")) %>% cbind(CT_Qs[1]) 
# CT_QsM <- CT_QsM %>% select(ends_with("_Q")) %>% cbind(CT_QsM[1]) 
# CT_QsF <- CT_QsF %>% select(ends_with("_Q")) %>% cbind(CT_QsF[1]) 
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))

```
# CT atlas plot 
```{r Atlas plots CT}
#mk df 
area <- c("banks superior temporal", "caudal anterior cingulate",  "caudal middle frontal", "cuneus", "entorhinal", "frontal pole", "fusiform",
                   "inferior parietal", "inferior temporal", "insula", "isthmus cingulate", "lateraloccipital", "lateralorbito frontal", "lingual",
                   "medial orbito frontal", "middle temporal",  "para central", "parahippocampal","pars opercularis", "pars orbitalis",
                   "pars triangularis", "pericalcarine", "post central", "posterior cingulate", "pre central", "precuneus", 
                   "rostral anterior cingulate", "rostral middle frontal", "superior frontal", "superior parietal", "superior temporal",
                   "supramarginal",  "temporal pole", "transverse temporal")
left <- cbind(area, "left")
right <- cbind(area, "right")
hemis <- rbind(left, right) 
colnames(hemis) <- c("area", "hemi")

###### for VR
CTplotVR <- as.data.frame(CT_VR, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
CTplotVR_sig.raw <- subset(CTplotVR, as.numeric(VR_Age_padj_VR) < 0.05)
CTplotVR_sig.cor <- subset(CTplotVR, as.numeric(VR_Full_padj_VR) < 0.05)

#plot
CTa <- ggbrain(CTplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white", high="#006600", midpoint=1, limits=c(0.5, 1.5), 
                       breaks=seq(0.5,1.5,by=0.5)) + theme(axis.title.x = element_blank()) +
                        guides(fill=guide_colorbar(direction= "horizontal", title="VR", 
                        title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTb <- ggbrain(CTplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white", high="#006600", midpoint=1, limits=c(0.5, 1.5), 
                       breaks=seq(0.5,1.5,by=0.5)) + theme(axis.title.x = element_blank()) +
                        guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTa, CTb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CT_VR_plot <- plot_grid(CTa, CTb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#names and save
CT_VR_plot.file <- paste(outdir, "CTatlasVR.png", sep="/")
ggsave(CT_VR_plot.file, CT_VR_plot, dpi=300, width = 21, height = 12, units = "cm")

####### for mean
CTplot.df <- as.data.frame(CT_out_tbl, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
CTplot_sig.raw <- subset(CTplot.df, as.numeric(AgeResid_Padj) < 0.05)
CTplot_sig.cor <- subset(CTplot.df, as.numeric(FullResid_Padj) < 0.05)

#plot
CTc <- ggbrain(CTplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-0.5, 0.5), 
                       breaks=seq(-0.5,0.5,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="Cohen's d", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTd <- ggbrain(CTplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-0.5, 0.5), 
                       breaks=seq(-0.5,0.5,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTc, CTd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CT_plot <- plot_grid(CTc, CTd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CT_plot.file <- paste(outdir, "CTatlas.png", sep="/")
ggsave(CT_plot.file, CT_plot, dpi=300, width = 21, height = 12, units = "cm")

### for age*sex interaction
## subsets of data that was significant
CTplotX_sig.raw <- subset(CTplot.df, as.numeric(simpX_padj_XTBVheight) < 0.05)
CTplotX_sig.cor <- subset(CTplot.df, as.numeric(TBVX_padj_XTBVheight) < 0.05)
CTplotAGE_sig.raw <- subset(CTplot.df, as.numeric(simp_padj_age) < 0.05)
CTplotAGE_sig.cor <- subset(CTplot.df, as.numeric(TBV_padj_age) < 0.05)

#plot
CTe <- ggbrain(CTplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="F", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTf <- ggbrain(CTplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTe, CTf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CTX_plot <- plot_grid(CTe, CTf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CTX_plot.file <- paste(outdir, "CTageXsex.png", sep="/")
ggsave(CTX_plot.file, CTX_plot, dpi=300, width = 21, height = 12, units = "cm")

#plot
CTg <- ggbrain(CTplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="F", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTh <- ggbrain(CTplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTg, CTh, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CTAGE_plot <- plot_grid(CTg, CTh, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CTAGE_plot.file <- paste(outdir, "CTatlasAGE.png", sep="/")
ggsave(CTAGE_plot.file, CTAGE_plot, dpi=300, width = 21, height = 12, units = "cm")

```
# stats cortical SA mean
```{r mean stats SA} 
## SA simple with interactions
CortSA_simpX  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age*Sex, data=SA.df)
})

## Cort simple
CortSA_simp  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age +Sex, data=SA.df)
})

### make df including residuals from TBV 
SA.res <- SA.df
SAres_age  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age, data=SA.res)
})
SAres_TBV  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=SA.res)
})
SAres_Full  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age, data=SA.res)
})

for (i in 1:length(CortLR)) {
  res <- augment(SAres_age[[i]])
  names(res) <- paste0(CortLR[i],"age",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(SAres_TBV[[i]])
  names(res) <- paste0(CortLR[i],"TBV",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(SAres_Full[[i]])
  names(res) <- paste0(CortLR[i],"Full",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[6]))
}

SAres_age_ls <-SA.res %>% select(contains("age.resid")) %>% names
SAres_TBV_ls <-SA.res %>% select(contains("TBV.resid")) %>% names
SAres_full_ls <-SA.res %>% select(contains("Full.resid")) %>% names

SA_age  <- lapply(SAres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=SA.res)
})
CortSA_TBV  <- lapply(SAres_TBV_ls, function(i){
  lm(get(i) ~ Age + Sex , data=SA.res)
})
CortSA_TBVX  <- lapply(SAres_TBV_ls, function(i){
  lm(get(i) ~ Age*Sex , data=SA.res)
})
SA_full  <- lapply(SAres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=SA.res)
})

## SA hemi
CortSA_hemi  <- lapply(Cort, function(i){
  lmer(get(i) ~ Age + Sex*hemi + (1|RID), data=SA.hemi)
})

SAmodels <- c("CortSA_simpX", "CortSA_simp", "CortSA_TBV", "CortSA_TBVX")

numSA=length(CortLR) #set how many corrections
SA_out <- extract(SAmodels, numSA)
SA_simpX <- SA_out[[1]]
SA_simp <- SA_out[[2]]
SA_TBV <- SA_out[[3]]
SA_TBVX <- SA_out[[4]]
SA_hemi <- extract_lmer(CortSA_hemi) 

names(SA_simpX) <- paste0('simpX_',names(SA_simpX))
names(SA_simp) <- paste0('simp_',names(SA_simp))
names(SA_TBV) <- paste0('TBV_',names(SA_TBV))
names(SA_TBVX) <- paste0('TBVX_',names(SA_TBVX))
names(SA_hemi) <- paste0('hemi_',names(SA_hemi)) 

SAresid_age <- extractT(SA_age, numSA)
names(SAresid_age) <- paste0('AgeResid_',names(SAresid_age))
SAresid_full <- extractT(SA_full, numSA)
names(SAresid_full) <- paste0('FullResid_',names(SAresid_full))

## merge and write out
SA_out_tbl <- cbind(SA_simpX, SA_simp, SA_TBV, SA_TBVX, SAresid_age, SAresid_full, SA_hemi) 
SA_out_tbl <- apply(SA_out_tbl,2,as.character)
rownames(SA_out_tbl) <- CortLR
SAout.file <- paste(outdir, "SA.csv", sep="/")
write.csv(SA_out_tbl, file=SAout.file, row.names = T)

```
# SA variance testing
```{r VR stats SA}
SA.M <- subset(SA.df, Sex == "Male") # 
SA.F <- subset(SA.df, Sex == "Female")

SACort_var  <- lapply(CortLR, function(i){
  var.test(SA.M[[i]], SA.F[[i]])
})
SAvar <- extract_var(SACort_var, numSA)

SA.M.res <- subset(SA.res, Sex == "Male") # 
SA.F.res <- subset(SA.res, Sex == "Female")

SACort_var.resAge  <- lapply(SAres_age_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resAge <- extract_var(SACort_var.resAge, numSA)

SACort_var.resTBV  <- lapply(SAres_TBV_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resTBV <- extract_var(SACort_var.resTBV, numSA)

SACort_var.resfull  <- lapply(SAres_full_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resfull <- extract_var(SACort_var.resfull, numSA)

# write out
names(SAvar) <- paste0('VR_',names(SAvar))
names(SAvar.resAge) <- paste0('VR_Age_',names(SAvar.resAge))
names(SAvar.resTBV) <- paste0('VR_TBV_',names(SAvar.resTBV))
names(SAvar.resfull) <- paste0('VR_Full_',names(SAvar.resfull))

SA_VR <- cbind(SAvar, SAvar.resAge, SAvar.resTBV, SAvar.resfull)
SA_VR <- apply(SA_VR,2,as.character)
rownames(SA_VR) <- CortLR
SAoutVR.file <- paste(outdir, "SA_VR.csv", sep="/")
write.csv(SA_VR, file=SAoutVR.file, row.names = T)

```
# plot SA - raw (for age plots) and minus age (box and vio)
```{r plots SA}
#mk df with hemis and resids
SA.R.res <- SA.res %>% select(starts_with("R_")) %>% cbind(SA.res[1])
colnames(SA.R.res) <- sub("R_", "", colnames(SA.R.res)) 
SA.R.res$hemi <- "right" 

SA.L.res <- SA.res %>% select(starts_with("L_")) %>% cbind(SA.res[1])
colnames(SA.L.res) <- sub("L_", "", colnames(SA.L.res)) 
SA.L.res$hemi <- "left" 

SA.hemi.res <- rbind(SA.R.res, SA.L.res)
SA.hemi.res <- merge(SA.hemi.res, demogs, by=("RID")) 

#make lits of variable names to graph based of resids
SA_to_graph_age <-SA.hemi.res %>% dplyr::select(contains("age.resid")) %>% names
SA_to_graph_TBV <-SA.hemi.res %>% dplyr::select(contains("TBV.resid")) %>% names
SA_to_graph_full <-SA.hemi.res %>% dplyr::select(contains("Full.resid")) %>% names

#plot
SAplots_box <- plot_box_hemi(SA_to_graph_age, SA.hemi.res)
SAplots_age <- plot_age_hemi(Cort, SA.hemi)
SAplots_vio <- plot_vio_hemi(SA_to_graph_age, SA.hemi.res)

#check arrangement
marrangeGrob(grobs=SAplots_box, ncol =3, nrow =3)
marrangeGrob(grobs=SAplots_age, ncol =2, nrow =2)
marrangeGrob(grobs=SAplots_vio, ncol =3, nrow =3)

#set arrangement
SA1 <- marrangeGrob(grobs=SAplots_box, ncol =3, nrow =5)
SA2 <- marrangeGrob(grobs=SAplots_age, ncol =2, nrow =4)
SA3 <- marrangeGrob(grobs=SAplots_vio, ncol =3, nrow =5)

#set file names
SAfile.box <- paste(outdir, "SAgraphBox.pdf", sep="/")
SAfile.age <- paste(outdir, "SAgraphAge.pdf", sep="/")
SAfile.vio <- paste(outdir, "SAgraphVio.pdf", sep="/")

#save
ggsave(SAfile.box, SA1, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.age, SA2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.vio, SA3, dpi=300, width = 21, height = 29.7, units = "cm")

```

# SA Plots - minus TBV (age plots), minus age and TBV (vio)
```{r plots SA without TBV}
#plot
SAplots_age.res <- plot_age_hemi(SA_to_graph_TBV, SA.hemi.res)
SAplots_vio.res <- plot_vio_hemi(SA_to_graph_full, SA.hemi.res)

#arrange
marrangeGrob(grobs=SAplots_age.res, ncol = 2, nrow =2)
marrangeGrob(grobs=SAplots_vio.res, ncol = 3, nrow =3)

#set arrangement
SA2.res <- marrangeGrob(grobs=SAplots_age.res, ncol =2, nrow =4)
SA3.res <- marrangeGrob(grobs=SAplots_vio.res, ncol =3, nrow =5)

#set file names
SAfile.age.res <- paste(outdir, "SAgraphAgeRES.pdf", sep="/")
SAfile.vio.res <- paste(outdir, "SAgraphVioRES.pdf", sep="/")

#save
ggsave(SAfile.age.res, SA2.res, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.vio.res, SA3.res, dpi=300, width = 21, height = 29.7, units = "cm")

```
# top/bottom subs SA
```{r top & bottom quantiles SA}
##Q1 is smallest Q20 largest
#SAres_full_ls list to use
# 
# SA_Qs <- mutate_at(SA.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SA_QsM <- mutate_at(SA.M.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SA_QsF <- mutate_at(SA.F.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# SA_Qs <- SA_Qs %>% select(ends_with("_Q")) %>% cbind(SA_Qs[1]) 
# SA_QsM <- SA_QsM %>% select(ends_with("_Q")) %>% cbind(SA_QsM[1]) 
# SA_QsF <- SA_QsF %>% select(ends_with("_Q")) %>% cbind(SA_QsF[1]) 
# 
# colnames(SA_Qs) <- sub("_Q", "_Q_SA", colnames(SA_Qs))
# colnames(SA_QsM) <- sub("_Q", "_Q_SA", colnames(SA_QsM))
# colnames(SA_QsF) <- sub("_Q", "_Q_SA", colnames(SA_QsF))
# 
# ## merge quantile scores from each modality
# Qovsc <- merge(OV_Qs, SC_Qs, by="Subject")
# QovscM <- merge(OV_QsM, SC_QsM, by="Subject")
# QovscF <- merge(OV_QsF, SC_QsF, by="Subject")
# Qcort <- merge(CT_Qs, SA_Qs, by="Subject")
# QcortM <- merge(CT_QsM, SA_QsM, by="Subject")
# QcortF <- merge(CT_QsF, SA_QsF, by="Subject")
# HCP_Qs <- merge(Qovsc, Qcort, by="Subject")
# HCP_QsM <- merge(QovscM, QcortM, by="Subject")
# HCP_QsF <- merge(QovscF, QcortF, by="Subject")
# 
# #make lowest quant=-1 and highest =1. everything else = 0. Sum 
# HCP_Qs_bin <- HCP_Qs 
# HCP_Qs_bin[HCP_Qs_bin == 1] <- -1
# HCP_Qs_bin[HCP_Qs_bin == 20] <- 1
# HCP_Qs_bin[HCP_Qs_bin > 1 & HCP_Qs_bin < 20] <- 0
# HCP_Qs_bin$sum <- rowSums(HCP_Qs_bin[,c(2:156)], na.rm=TRUE)
# 
# HCP_Qs_binM <- HCP_QsM 
# HCP_Qs_binM[HCP_Qs_binM == 1] <- -1
# HCP_Qs_binM[HCP_Qs_binM == 20] <- 1
# HCP_Qs_binM[HCP_Qs_binM > 1 & HCP_Qs_binM < 20] <- 0
# HCP_Qs_binM$sum <- rowSums(HCP_Qs_binM[,c(2:156)], na.rm=TRUE)
# 
# HCP_Qs_binF <- HCP_QsF 
# HCP_Qs_binF[HCP_Qs_binF == 1] <- -1
# HCP_Qs_binF[HCP_Qs_binF == 20] <- 1
# HCP_Qs_binF[HCP_Qs_binF > 1 & HCP_Qs_binF < 20] <- 0
# HCP_Qs_binF$sum <- rowSums(HCP_Qs_binF[,c(2:156)], na.rm=TRUE)
# 
# #melt to long form 
# HCP_Qlong <-melt(HCP_Qs_bin, id.vars=c("Subject", "sum"))
# HCP_QlongM <-melt(HCP_Qs_binM, id.vars=c("Subject", "sum"))
# HCP_QlongF <-melt(HCP_Qs_binF, id.vars=c("Subject", "sum"))
# 
# # ### filter to only keep highest and lowest?
# # HCP_Qlong$filt[HCP_Qlong$value == 1] <- "-1"
# # HCP_Qlong$filt[HCP_Qlong$value == 20] <- "1"
# # HCP_QlongM$filt[HCP_QlongM$value == 1] <- "-1"
# # HCP_QlongM$filt[HCP_QlongM$value == 20] <- "1"
# # HCP_QlongF$filt[HCP_QlongF$value == 1] <- "-1"
# # HCP_QlongF$filt[HCP_QlongF$value == 20] <- "1"
# 
# ##re-order data
# HCP_Qlong <- HCP_Qlong[order(HCP_Qlong$sum),]
# HCP_QlongM <- HCP_QlongM[order(HCP_QlongM$value, HCP_QlongM$variable),]
# HCP_QlongF <- HCP_QlongF[order(HCP_QlongF$value, HCP_QlongF$variable),]
# 
# 
# 
# #### fix colours and order
# ggplot(HCP_Qlong, aes(x=as.factor(Subject), y=variable, fill=sum)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# M1 <- ggplot(HCP_QlongM, aes(x=as.factor(Subject), y=variable, fill=filt)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# M2 <- ggplot(HCP_QlongF, aes(x=as.factor(Subject), y=variable, fill=filt)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# plot_grid(M1, M2, align="hv", ncol = 2, labels=c('A', 'B'), label_size=10)
# plt <- plot_grid(M1, M2, align="hv", ncol = 2, labels=c('A', 'B'),label_size=10)
# 
# #name and save
# CTX_plot.file <- paste(outdir, "CTageXsex.png", sep="/")
# ggsave(CTX_plot.file, CTX_plot, dpi=300, width = 21, height = 12, units = "cm")
# 
# 

```

# SA atlas plot 
```{r Atlas plots SA}
area <- c("banks superior temporal", "caudal anterior cingulate",  "caudal middle frontal", "cuneus", "entorhinal", "frontal pole", "fusiform",
                   "inferior parietal", "inferior temporal", "insula", "isthmus cingulate", "lateraloccipital", "lateralorbito frontal", "lingual",
                   "medial orbito frontal", "middle temporal",  "para central", "parahippocampal","pars opercularis", "pars orbitalis",
                   "pars triangularis", "pericalcarine", "post central", "posterior cingulate", "pre central", "precuneus", 
                   "rostral anterior cingulate", "rostral middle frontal", "superior frontal", "superior parietal", "superior temporal",
                   "supramarginal",  "temporal pole", "transverse temporal")

left <- cbind(area, "left")
right <- cbind(area, "right")
hemis <- rbind(left, right) 
colnames(hemis) <- c("area", "hemi")

SAplotVR <- as.data.frame(SA_VR, stringsAsFactors = F) %>% cbind(hemis)

## select subset of sig data
SAplotVR_sig.raw <- subset(SAplotVR, as.numeric(VR_Age_padj_VR) < 0.05)
SAplotVR_sig.cor <- subset(SAplotVR, as.numeric(VR_Full_padj_VR) < 0.05)

#plot
SAa <- ggbrain(SAplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1,  limits=c(0.5, 2.7), 
                       breaks=seq(0.5,2.7,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="VR", direction = "horizontal", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
SAb <- ggbrain(SAplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1, limits=c(0.5, 2.7), 
                      breaks=seq(0.5,2.7,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAa,SAb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_VR_plot <- plot_grid(SAa,SAb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#names and save
SA_VR_plot.file <- paste(outdir, "SAatlasVR.png", sep="/")
ggsave(SA_VR_plot.file, SA_VR_plot, dpi=300, width = 21, height = 12, units = "cm")

####### for mean
SAplot.df <- as.data.frame(SA_out_tbl, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
SAplot_sig.raw <- subset(SAplot.df, as.numeric(AgeResid_Padj) < 0.05)
SAplot_sig.cor <- subset(SAplot.df, as.numeric(FullResid_Padj) < 0.05)

#plot
SAc <- ggbrain(SAplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-1.3, 1), 
                      breaks=seq(-1,1,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", direction = "horizontal", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
SAd <- ggbrain(SAplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-1.3, 1), 
                      breaks=seq(-1,1,by=0.5)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAc, SAd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_plot <- plot_grid(SAc, SAd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
SA_plot.file <- paste(outdir, "SAatlas.png", sep="/")
ggsave(SA_plot.file, SA_plot, dpi=300, width = 21, height = 12, units = "cm")


######### for age
## subsets of data that was significant
SAplotAGE_sig.raw <- subset(SAplot.df, as.numeric(simp_padj_age) < 0.05)
SAplotAGE_sig.cor <- subset(SAplot.df, as.numeric(TBV_padj_age) < 0.05)
SAplotX_sig.raw <- subset(SAplot.df, as.numeric(simpX_padj_XTBVheight) < 0.05)
SAplotX_sig.cor <- subset(SAplot.df, as.numeric(TBVX_padj_XTBVheight) < 0.05)

#plot
SAe <- ggbrain(SAplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(axis.title.x = element_blank())+ 
  guides(fill=guide_colorbar(title="F", direction = "horizontal", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
SAf <- ggbrain(SAplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAe, SAf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_plotAGE <- plot_grid(SAe, SAf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
SA_plotAGE.file <- paste(outdir, "SAatlasAGE.png", sep="/")
ggsave(SA_plotAGE.file, SA_plotAGE, dpi=300, width = 21, height = 12, units = "cm")
```

# unit sphere stuff
```{r write out residual files}
colnames(CT.res) <- paste0("CT_", colnames(CT.res))
colnames(SA.res) <- paste0("SA_", colnames(SA.res))

All.res <- merge(Vol.res, SC.res, by="RID") %>% merge(CT.res, by.x="RID", by.y="CT_RID") %>% 
  merge(SA.res, by.x="RID", by.y="SA_RID") %>% 
  select(contains("Full.resid")) %>% cbind(Vol.res[c("RID", "Age", "Sex")]) 

Allres.file <- paste(outdir, "Allres.csv", sep="/")
write.csv(All.res, file=Allres.file, row.names = T)

```

#Prep ADNI graphs for merging with HCP and PNC (FreeSurfer.Rmd)
```{r prep figures for combining}

#plot required HCP graphs without legends (the same is done for PNC at the end of that script)

##CT
ADNI_CTraw <- ggbrain(CTplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-0.5, 0.5), breaks=seq(-0.5,0.5,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())
ADNI_CTcor <- ggbrain(CTplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-0.5, 0.5), breaks=seq(-0.5,0.5,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())

ADNI_CTrawVR <- ggbrain(CTplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1, limits=c(0.5, 1.5), breaks=seq(0.5,1.5,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())
ADNI_CTcorVR <- ggbrain(CTplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1, limits=c(0.5, 1.5), breaks=seq(0.5,1.5,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())

ADNI_CTrawAGExSEX <- ggbrain(CTplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(legend.position="none", axis.title.x = element_blank()) 
ADNI_CTcorAGExSEX <- ggbrain(CTplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(legend.position="none", axis.title.x = element_blank()) 

ADNI_CTrawAGE <- ggbrain(CTplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(legend.position="none", axis.title.x = element_blank()) 
ADNI_CTcorAGE <- ggbrain(CTplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(legend.position="none", axis.title.x = element_blank()) 

##SA
ADNI_SAraw <- ggbrain(SAplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-1.3, 1), breaks=seq(-1,1,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())
ADNI_SAcor <- ggbrain(SAplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="#FFFF99", high="#FF3300", midpoint=0, limits=c(-1.3, 1), breaks=seq(-1,1,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())

ADNI_SArawVR <- ggbrain(SAplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1, limits=c(0.5, 2.7), breaks=seq(0.5,2.7,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())
ADNI_SAcorVR <- ggbrain(SAplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#9900CC", mid="white",  high="#006600", midpoint=1, limits=c(0.5, 2.7), breaks=seq(0.5,2.7,by=0.5)) + 
  theme(legend.position="none", axis.title.x = element_blank())
  
ADNI_SArawAGE <- ggbrain(SAplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(legend.position="none", axis.title.x = element_blank())
ADNI_SAcorAGE <- ggbrain(SAplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(legend.position="none", axis.title.x = element_blank()) 

ADNI_SArawAGExSEX <- ggbrain(SAplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 15), breaks=seq(0,15,by=5)) + theme(legend.position="none", axis.title.x = element_blank())
ADNI_SAcorAGExSEX <- ggbrain(SAplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 15), breaks=seq(0,15,by=5)) + theme(legend.position="none", axis.title.x = element_blank()) 

## rename ADNI OV & SC
ADNI_OVplots_vio <- OVplots_vio
ADNI_OVplots_vio.res <- OVplots_vio.res
ADNI_OVplots_age <- OVplots_age
ADNI_OVplots_age.res <- OVplots_age.res

ADNI_SCplots_vio <- SCplots_vio
ADNI_SCplots_vio.res <- SCplots_vio.res
ADNI_SCplots_age <- SCplots_age
ADNI_SCplots_age.res <- SCplots_age.res

```
