---
title: "FreeSurfer"
author: "nforde"
date: "August 9, 2018"
output: html_document
---
# get libraries/set paths
```{r}
library(tidyverse)
library(broom)
library(knitr)
library(car)
library(cowplot)
library(lme4)
library(ggseg)
library(gridExtra)
library(reshape2)

## set all the paths
#HCP
behaviour <- read.csv("/projects/nforde/HCP/clinical/demog_behaviour.csv")
restricted <- read.csv("/projects/nforde/HCP/clinical/RESTRICTED.csv")
FS <- read.csv("/projects/nforde/HCP/orig/FreeSurfer.csv")
# subs <- read.table("/projects/nforde/HCP/bin/subs.txt") #list of those with T1, rs-fMRI and dMRI

outdir <- "/projects/nforde/HCP/stats/HCP"

```
# define functions

```{r}
## for normalising data
transform_to_normal <- function(X) {
  # calculate the best exponent using powerTransform:
  pT <- powerTransform(X)
  # apply the power transform and save the result to a new variable
  X_pT <- X^pT$lambda ## note ^ is exponent in r
  return(X_pT)
}

## function to extract stats from lm
extract <- function(X,num){ 
  lapply(X, function(i){
    F_age <- lapply(get(i), function(f) Anova(f)$"F value"[1])
    F_sex <- lapply(get(i), function(f) Anova(f)$"F value"[2])
    F_XTBVheight <-lapply(get(i), function(f) Anova(f)$"F value"[3])
    p_age <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[1])
    p_sex <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[2])
    p_XTBVheight <-lapply(get(i), function(f) Anova(f)$"Pr(>F)"[3])
    adjRsq <- sapply(get(i), function(f) summary(f)$adj.r.squared)
    padj_age <- p.adjust(p_age, method="fdr", n=num)
    padj_sex <- p.adjust(p_sex, method="fdr", n=num)
    padj_XTBVheight <- p.adjust(p_XTBVheight, method="fdr", n=num)
    
    merged <- as.data.frame(cbind(F_age, padj_age, F_sex, padj_sex, F_XTBVheight, padj_XTBVheight, adjRsq))
    return(merged)
  })
}

## function to extract stats from lmer
extract_lmer <- function(i){ 
  Chi_age <- lapply((i), function(f) Anova(f)$"Chisq"[1])
  Chi_sex <- lapply((i), function(f) Anova(f)$"Chisq"[2])
  Chi_hemi <-lapply((i), function(f) Anova(f)$"Chisq"[3])
  Chi_sexXhemi <-lapply((i), function(f) Anova(f)$"Chisq"[4])
  p_age <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[1])
  p_sex <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[2])
  p_hemi <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[3])
  p_sexXhemi <-lapply((i), function(f) Anova(f)$"Pr(>Chisq)"[4])
  padj_age <- p.adjust(p_age, method="fdr")
  padj_sex <- p.adjust(p_sex, method="fdr")
  padj_hemi <- p.adjust(p_hemi, method="fdr")
  padj_sexXhemi <- p.adjust(p_sexXhemi, method="fdr")
    
  merged <- as.data.frame(cbind(Chi_age, padj_age, Chi_sex, padj_sex, Chi_hemi, padj_hemi, Chi_sexXhemi, padj_sexXhemi))
  return(merged)
}

extractT <- function(i, num){
  Tval <- lapply((i), function(f) f$statistic)
  Pval <- lapply((i), function(f) f$p.value)
  dof <- lapply((i), function(f) f$parameter)
   
  Padj <- p.adjust(Pval, method="fdr", n=num)
  Cohen <- (as.numeric(Tval)*2)/sqrt(as.numeric(dof))
  
  merged <- as.data.frame(cbind(Tval, Padj, Cohen))
  return(merged)

}

## function to extract stats from var.test
extract_var <- function(X, num){ 
  VR <- lapply(X, function(f) (f)$"estimate")
  VR_p <- lapply(X, function(f) (f)$"p.value")
  padj_VR <- p.adjust(VR_p, method="fdr", n=num)
  
  merged <- as.data.frame(cbind(VR, padj_VR))
  return(merged)
}


### function to plot and grid multiple figures
plot_box <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Sex, color= Sex)) + geom_boxplot(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none"))
  # grid <- do.call(grid.arrange, a)
  return(a)
} #

#same as above, split violin instead of box
plot_vio <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x="Sex", fill= Sex)) + geom_split_violin(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text.y=element_text(size=8),
                      axis.title=element_text(size=10), legend.position="none")
              +stat_summary(aes_string(y=f), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", shape =95, 
                            size=0.5, position = position_dodge(width = .75)))
  return(a)
} #
# 
# +stat_summary(aes_string(y="Caudate"), fun.y=mean, geom="point", shape=23, size=2, position = position_dodge(width = .75))

# +stat_summary(aes_string(y="Caudate"), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", size=1, position = position_dodge(width = .75))


plot_age <- function(ROIs,df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Age_in_Yrs, color =Sex)) +xlab("Age (years)") 
              + theme(axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none") 
              + geom_jitter(aes_string(y=f), width=0.2, size= 0.5) + geom_smooth(aes_string(y=f), span = 0.5))
  return(a)
}

### function to plot measure by sex, grouped by hemisphere
plot_box_hemi <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=hemi, fill = Sex)) + geom_boxplot(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none"))
  return(a)
} #

#same as above, split violin instead of box
plot_vio_hemi <- function(ROIs, df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=hemi, fill = Sex)) + geom_split_violin(aes_string(y=f)) 
              + theme(axis.title.x = element_blank(), axis.text=element_text(size=8), axis.title=element_text(size=10), legend.position="none") 
              +stat_summary(aes_string(y=f), fun.data=mean_sdl, fun.args = list(mult = 1), geom="pointrange", shape =95, size=0.5, 
                            position = position_dodge(width = .75)))
  return(a)
} #

# + scale_x_discrete(labels= c("Female","Male"))  + theme(axis.title.x = element_blank())
# plot X by age and gender
plot_age_hemi <- function(ROIs,df) {
  a <- lapply(ROIs, function(f) ggplot(df, aes(x=Age_in_Yrs, color =Sex)) +xlab("Age (years)") 
              + geom_jitter(aes_string(y=f), width=0.2, size= 0.5) + geom_smooth(aes_string(y=f), span = 0.5) 
              + facet_grid(. ~hemi , scales = "free_y")
              + theme(axis.text=element_text(size=10), axis.title=element_text(size=12), legend.position="none", 
                      strip.text = element_text(size=12)))
  return(a)
}

#+ xlab("Age (years)") + scale_shape_manual(values=c(4,1)) #change shapes,  scale_linetype_manual(values=c("dotdash", "dotted")) # Change linetypes
#legend.position="none", , strip.background = element_rect(size= 3)

# a<-  + geom_boxplot(outlier.shape = NA, lwd=0.3)
# b <- scale_x_discrete(labels= c("HmarrangeGrobC","ADHD","TS"))
# c <- a +b   + theme(legend.text=element_text(size=4), axis.title.x = element_blank(), axis.title.y = element_text(size=5), axis.text.x=element_text(size=4, colour="black"), axis.text.y = element_text(size=4, colour="black"),plot.title=element_text(size=6)) + ylab("FA") +guides(fill=FALSE) +scale_fill_manual(values=c("grey","white"))+ ylim(0.2,0.45)              
# grid <- theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank())
# ggsave(file="C:/Users/p270073/Dropbox/work/data/Compuls/dMRI/graph.pdf",g, width=8, height=10, dpi=300)
# save_plot

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1,'group']
  newdata <- plyr::arrange(transform(data, x = if(grp%%2==1) xminv else xmaxv), if(grp%%2==1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1,nrow(newdata)-1,nrow(newdata)), 'x'] <- round(newdata[1, 'x']) 
  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 
                                              1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, position = position, show.legend = show.legend, inherit.aes = inherit.aes, params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}

```
# organise
```{r}
demog <- merge(behaviour, restricted, by = "Subject")
# demog <- merge(demog, subs, by.x = "Subject", by.y = "V1")
demogs <- filter(demog, !grepl('C', QC_Issue)) # remove those rated C; head coil instability

demogs$Sex <- NA
demogs$Sex[demogs$Gender=="M"] <- "Male"  
demogs$Sex[demogs$Gender=="F"] <- "Female" 

# calc total cerebellum wm and gm vol
FS$FS_Cerebellum_Cort_Vol <- (FS$FS_L_Cerebellum_Cort_Vol + FS$FS_R_Cerebellum_Cort_Vol) ################
FS$FS_Cerebellum_WM_Vol <- (FS$FS_L_Cerebellum_WM_Vol + FS$FS_R_Cerebellum_WM_Vol) ##############

# Isolate vol measures and separate out hemis  
Vol.df <- FS %>% select(contains("Vol")) %>% cbind(FS[1]) 
colnames(Vol.df) <- sub("FS_", "", colnames(Vol.df)) 
colnames(Vol.df) <- sub("_Vol", "", colnames(Vol.df)) 

Vol.R <- Vol.df %>% select(starts_with("R_")) %>% cbind(FS[1])
colnames(Vol.R) <- sub("R_", "", colnames(Vol.R)) 
Vol.R$hemi <- "right" 

Vol.L <- Vol.df %>% select(starts_with("L_")) %>% cbind(FS[1])
colnames(Vol.L) <- sub("L_", "", colnames(Vol.L)) 
Vol.L$hemi <- "left" 

Vol.hemi <- rbind(Vol.R, Vol.L)

Vol.df <- merge(Vol.df, demogs, by=("Subject"))
Vol.hemi <- merge(Vol.hemi, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))
# Vol.R <- merge(Vol.R, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))
# Vol.L <- merge(Vol.L, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))

## Cortical thickness
CT.df <- FS %>% select(contains("Thck")) %>% cbind(FS[1]) 
colnames(CT.df) <- sub("FS_", "", colnames(CT.df)) 
colnames(CT.df) <- sub("_Thck", "", colnames(CT.df)) 

CT.R <- CT.df %>% select(starts_with("R_")) %>% cbind(FS[1])
colnames(CT.R) <- sub("R_", "", colnames(CT.R)) 
CT.R$hemi <- "right" 

CT.L <- CT.df %>% select(starts_with("L_")) %>% cbind(FS[1])
colnames(CT.L) <- sub("L_", "", colnames(CT.L)) 
CT.L$hemi <- "left" 

CT.hemi <- rbind(CT.R, CT.L)

CT.df <- merge(CT.df, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))
CT.hemi <- merge(CT.hemi, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))


### Surface Area
SA.df <- FS %>% select(contains("Area")) %>% cbind(FS[1])
colnames(SA.df) <- sub("FS_", "", colnames(SA.df)) 
colnames(SA.df) <- sub("_Area", "", colnames(SA.df)) 

SA.R <- SA.df %>% select(starts_with("R_")) %>% cbind(FS[1])
colnames(SA.R) <- sub("R_", "", colnames(SA.R)) 
SA.R$hemi <- "right" 

SA.L <- SA.df %>% select(starts_with("L_")) %>% cbind(FS[1])
colnames(SA.L) <- sub("L_", "", colnames(SA.L)) 
SA.L$hemi <- "left" 

SA.hemi <- rbind(SA.L, SA.R)

SA.df <- merge(SA.df, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))
SA.hemi <- merge(SA.hemi, demogs, by=("Subject")) %>% merge(Vol.df[c(1,4)], by=("Subject"))

### lists of variables
overall <- c("Total_GM", "Tot_WM", "Cerebellum_Cort", "Cerebellum_WM") ###########################
overallincTBV <- c("BrainSeg_No_Vent", "Total_GM", "Tot_WM", "Cerebellum_Cort", "Cerebellum_WM") ###############
SubCortLR <- c("L_ThalamusProper", "L_Caudate", "L_Putamen", "L_Pallidum", "L_Hippo", "L_Amygdala", "L_AccumbensArea", "R_ThalamusProper", "R_Caudate", "R_Putamen",  "R_Pallidum", "R_Hippo",  "R_Amygdala", "R_AccumbensArea")
SubCort <- c("ThalamusProper", "Caudate", "Putamen", "Pallidum", "Hippo", "Amygdala", "AccumbensArea")
CC <- c("CC_Posterior", "CC_MidPosterior", "CC_Central", "CC_MidAnterior", "CC_Anterior")
CortLR <- names(CT.df)[2:69]
Cort <- names(CT.hemi)[2:35]
```
# Stats Overall
```{r}
### Total Brain Volume (BrainSeg_No_Vent) analysis
TBVsimpX <- lm(BrainSeg_No_Vent ~ Age_in_Yrs*Sex, data=Vol.df)
TBVsimp <- lm(BrainSeg_No_Vent ~ Age_in_Yrs + Sex, data=Vol.df)
TBVageres <- lm(BrainSeg_No_Vent ~ Age_in_Yrs, data=Vol.df)
TBVageres1 <- augment(TBVageres)
TBVageres.df <- cbind(Vol.df, TBVageres1)
TBVage <- t.test(.resid ~ Sex, data=TBVageres.df)

TBVmods <- list(TBVsimpX, TBVsimp)

## TBV extract measures
F_age <- lapply(TBVmods, function(f) Anova(f)$"F value"[1])
F_sex <- lapply(TBVmods, function(f) Anova(f)$"F value"[2])
F_Xheight <-lapply(TBVmods, function(f) Anova(f)$"F value"[3])
p_age <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[1])
p_sex <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[2])
p_Xheight <-lapply(TBVmods, function(f) Anova(f)$"Pr(>F)"[3])
adjRsq <- sapply(TBVmods, function(f) summary(f)$adj.r.squared)
padj_age <- p.adjust(p_age, method="fdr", n=5) ############
padj_sex <- p.adjust(p_sex, method="fdr", n=5) ############
padj_Xheight <- p.adjust(p_Xheight, method="fdr", n=5) ############

TBVt <- TBVage$statistic
TBVp <- TBVage$p.value
TBVdof <- TBVage$parameter
TBVpadj <- p.adjust(TBVp, method="fdr", n=5) ############
TBVCohen <- (as.numeric(TBVt)*2)/sqrt(as.numeric(TBVdof))

TBV_out <- as.data.frame(cbind(F_age, padj_age, F_sex, padj_sex, F_Xheight, padj_Xheight, adjRsq, TBVt, TBVpadj, TBVCohen))
TBV_out <- apply(TBV_out,2,as.character)
TBVout.file <- paste(outdir, "TBV.csv", sep="/")
write.csv(TBV_out, file=TBVout.file, row.names = F)

###### total GM and total WM 

## overall simple with interactions
overall_simpX  <- lapply(overall, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex, data=Vol.df)
})
## overall simple
overall_simp  <- lapply(overall, function(i){
  lm(get(i) ~ Age_in_Yrs +Sex, data=Vol.df)
})

### make df including residuals from TBV and height mods
# Vol.res <- subset(Vol.df, ! is.na(Height))
Vol.res <- Vol.df

OVres_age  <- lapply(overall, function(i){
  lm(get(i) ~ Age_in_Yrs, data=Vol.res)
})
OVres_TBV  <- lapply(overall, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=Vol.res)
})
OVres_full  <- lapply(overall, function(i){
  lm(get(i) ~ BrainSeg_No_Vent +Age_in_Yrs, data=Vol.res)
})

for (i in 1:length(overall)) {
  res <- augment(OVres_age[[i]])
  names(res) <- paste0(overall[i],"age",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[5]))
}
for (i in 1:length(overall)) {
  res <- augment(OVres_TBV[[i]])
  names(res) <- paste0(overall[i],"TBV",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[5]))
}
for (i in 1:length(overall)) {
  res <- augment(OVres_full[[i]])
  names(res) <- paste0(overall[i],"Full",names(res))
  Vol.res <- cbind(Vol.res, as.data.frame(res[6]))
}

OVres_age_ls <-Vol.res %>% select(contains("age.resid")) %>% names
OVres_TBV_ls <-Vol.res %>% select(contains("TBV.resid")) %>% names
OVres_full_ls <-Vol.res %>% select(contains("Full.resid")) %>% names

overall_age  <- lapply(OVres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=Vol.res)
})
overall_TBV  <- lapply(OVres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs + Sex , data=Vol.res)
})
overall_TBVX  <- lapply(OVres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex , data=Vol.res)
})
overall_full  <- lapply(OVres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=Vol.res)
})

OVmodels <- c("overall_simpX", "overall_simp", "overall_TBV", "overall_TBVX")

overall_out <- extract(OVmodels, 5) ################
OV_simpX <- overall_out[[1]]
OV_simp <- overall_out[[2]]
OV_TBV <- overall_out[[3]]
OV_TBVX <- overall_out[[4]]

names(OV_simpX) <- paste0('simpX_',names(OV_simpX))
names(OV_simp) <- paste0('simp_',names(OV_simp))
names(OV_TBV) <- paste0('TBV_',names(OV_TBV))
names(OV_TBVX) <- paste0('TBVX_',names(OV_TBVX))

OVresid_age <- extractT(overall_age, 5) ############
names(OVresid_age) <- paste0('AgeResid',names(OVresid_age))
OVresid_full <- extractT(overall_full, 5) ############
names(OVresid_full) <- paste0('FullResid',names(OVresid_full))

### merge and write out
OV_out <- cbind(OV_simpX, OV_simp, OV_TBV, OV_TBVX, OVresid_age, OVresid_full)
OV_out <- apply(OV_out,2,as.character)
rownames(OV_out) <- overall
OVout.file <- paste(outdir, "overall.csv", sep="/")
write.csv(OV_out, file=OVout.file, row.names = T)

```
# Overall variance testing
```{r}
# raw model
Vol.M <- subset(Vol.res, Sex == "Male")
Vol.F <- subset(Vol.res, Sex == "Female")

TBVageres.M <- subset(TBVageres.df, Sex == "Male")
TBVageres.F <- subset(TBVageres.df, Sex == "Female")

# for TBV only
TBV_var <- var.test(Vol.M$BrainSeg_No_Vent, Vol.F$BrainSeg_No_Vent)
TBV_est <- TBV_var$estimate
TBV_VRp <- TBV_var$p.value
TBV_VRpadj <- p.adjust(TBV_VRp, method="fdr", n=5) ######

TBVres_var <- var.test(TBVageres.M$BrainSeg_No_Vent, TBVageres.F$BrainSeg_No_Vent)
TBVres_est <- TBVres_var$estimate
TBVres_VRp <- TBVres_var$p.value
TBVres_VRpadj <- p.adjust(TBV_VRp, method="fdr", n=5) ###########

TBV_VR <- cbind(TBV_est, TBV_VRpadj,TBVres_est, TBVres_VRpadj) 
OVoutTBV_VR.file <- paste(outdir, "TBV_VR.csv", sep="/")
write.csv(TBV_VR, file=OVoutTBV_VR.file, row.names = T)

# for the rest of the overall measures
overall_var  <- lapply(overall, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar <- extract_var(overall_var, 5)###########

# residual mods
overall_var.resAge  <- lapply(OVres_age_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resAge <- extract_var(overall_var.resAge, 5)###########

overall_var.resTBV  <- lapply(OVres_TBV_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resTBV <- extract_var(overall_var.resTBV, 5)###########

overall_var.resfull  <- lapply(OVres_full_ls, function(i){
  var.test(Vol.M[[i]], Vol.F[[i]])
})
OVvar.resfull <- extract_var(overall_var.resfull, 5)###########

# write out
names(OVvar) <- paste0('VR_',names(OVvar))
names(OVvar.resAge) <- paste0('VR_Age_',names(OVvar.resAge))
names(OVvar.resTBV) <- paste0('VR_TBV_',names(OVvar.resTBV))
names(OVvar.resfull) <- paste0('VR_Full_',names(OVvar.resfull))

OV_VR <- cbind(OVvar, OVvar.resAge, OVvar.resTBV, OVvar.resfull)
OV_VR <- apply(OV_VR,2,as.character)
rownames(OV_VR) <- overall
OVoutVR.file <- paste(outdir, "overallVR.csv", sep="/")
write.csv(OV_VR, file=OVoutVR.file, row.names = T)

```
# Overall Plots raw (for age plots) and minus age (box and vio)
```{r}
OVplots_age <- plot_age(overallincTBV, Vol.df)

OV_to_graph_age <- c("BrainSeg_No_Vent", "Total_GMage.resid", "Tot_WMage.resid", "Cerebellum_Cortage.resid", "Cerebellum_WMage.resid") #########
OVplots_box <- plot_box(OV_to_graph_age, Vol.res)
OVplots_vio <- plot_vio(OV_to_graph_age, Vol.res) 

plot_grid(plotlist=OVplots_age, align="hv", ncol = 3)  
plot_grid(plotlist=OVplots_box, align="hv", ncol = 3)
plot_grid(plotlist=OVplots_vio, align="hv", ncol = 3)

OV2 <- plot_grid(plotlist=OVplots_age, align="hv", ncol = 3)  
OV1 <- plot_grid(plotlist=OVplots_box, align="hv", ncol = 3)
OV3 <- plot_grid(plotlist=OVplots_vio, align="hv", ncol = 3)

OVfile.box <- paste(outdir, "OVgraphBox.png", sep="/")
OVfile.age <- paste(outdir, "OVgraphAge.png", sep="/")
OVfile.vio <- paste(outdir, "OVgraphVio.png", sep="/")

ggsave(OVfile.box, OV1, dpi=300, width = 21, height = 14, units = "cm") #####
ggsave(OVfile.age, OV2, dpi=300, width = 21, height = 14, units = "cm") #####
ggsave(OVfile.vio, OV3, dpi=300, width = 21, height = 14, units = "cm") #####

```
# Overall Plots - minus TBV (age plots), minus age and TBV (vio)
```{r}

OV_to_graph_TBV <- c("BrainSeg_No_Vent", OVres_TBV_ls) 
OV_to_graph_full <- c("BrainSeg_No_Vent", OVres_full_ls) 

OVplots_age.res <- plot_age(OV_to_graph_TBV, Vol.res)
OVplots_vio.res <- plot_vio(OV_to_graph_full, Vol.res)

plot_grid(plotlist=OVplots_age.res, align="hv", ncol = 3)
plot_grid(plotlist=OVplots_vio.res, align="hv", ncol = 3)

OV2.res <- plot_grid(plotlist=OVplots_age.res, align="hv", ncol =3)
OV3.res <- plot_grid(plotlist=OVplots_vio.res, align="hv", ncol =3)

OVfile.age.res <- paste(outdir, "OVgraphAgeRES.png", sep="/")
OVfile.vio.res <- paste(outdir, "OVgraphVioRES.png", sep="/")

ggsave(OVfile.age.res, OV2.res, dpi=300, width = 21, height = 14, units = "cm") ######
ggsave(OVfile.vio.res, OV3.res, dpi=300, width = 21, height = 14, units = "cm") #########

#alt config
AltOV1 <- plot_grid((OVplots_vio[[1]] + ylab("Total Brain Volume")), (OVplots_vio[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_vio[[3]]+ ylab("Cerebral White Matter")), (OVplots_vio[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_vio[[5]]+ ylab("Cerebellar White Matter")), NULL ,(OVplots_vio.res[[2]]+ ylab("Cerebral Grey Matter")),  
                    (OVplots_vio.res[[3]]+ ylab("Cerebral White Matter")), (OVplots_vio.res[[4]]+ ylab("Cerebellar Grey Matter")),  
                    (OVplots_vio.res[[5]]+ ylab("Cerebellar White Matter")), align="hv", ncol =5, 
                    labels=c('A', 'B', 'C', 'D', 'E', ' ', 'F', 'G', 'H', 'I', 'J'), label_size=10)
AltOV2 <- plot_grid((OVplots_age[[1]]+ ylab("Total Brain Volume")), (OVplots_age[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_age[[3]]+ ylab("Cerebral White Matter")), (OVplots_age[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_age[[5]]+ ylab("Cerebellar White Matter")), NULL, (OVplots_age.res[[2]]+ ylab("Cerebral Grey Matter")), 
                    (OVplots_age.res[[3]]+ ylab("Cerebral White Matter")), (OVplots_age.res[[4]]+ ylab("Cerebellar Grey Matter")), 
                    (OVplots_age.res[[5]]+ ylab("Cerebellar White Matter")), align="hv", ncol =5, 
                    labels=c('A', 'B', 'C', 'D', 'E', ' ', 'F', 'G', 'H', 'I', 'J'), label_size=10)

OVfile.alt1 <- paste(outdir, "OVgraphVio_comb.png", sep="/")
OVfile.alt2 <- paste(outdir, "OVgraphAge_comb.png", sep="/")

ggsave(OVfile.alt1, AltOV1, dpi=300, width = 21, height = 8, units = "cm")
ggsave(OVfile.alt2, AltOV2, dpi=300, width = 30, height = 12, units = "cm")

```
# top/bottom subs OV
```{r}
##Q1 is smallest Q20 largest
#OV_to_graph_full list to use
# 
# OV_Qs <- mutate_at(Vol.res, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# OV_QsM <- mutate_at(Vol.M, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# OV_QsF <- mutate_at(Vol.F, OV_to_graph_full, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# OV_Qs <- OV_Qs %>% select(ends_with("_Q")) %>% cbind(OV_Qs[1]) 
# OV_QsM <- OV_QsM %>% select(ends_with("_Q")) %>% cbind(OV_QsM[1]) 
# OV_QsF <- OV_QsF %>% select(ends_with("_Q")) %>% cbind(OV_QsF[1]) 

```
# sub cortical stats mean 
```{r}
## Stats sub cort

## SubCort simple with interactions
subCort_simpX  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex, data=Vol.df)
})

## SubCort simple
subCort_simp  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age_in_Yrs +Sex, data=Vol.df)
})

### make df including residuals from TBV 
SC.res <- Vol.df
SCres_age  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ Age_in_Yrs, data=SC.res)
})
SCres_TBV  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=SC.res)
})
SCres_Full  <- lapply(SubCortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age_in_Yrs, data=SC.res)
})

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_age[[i]])
  names(res) <- paste0(SubCortLR[i],"age",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[5]))
}

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_TBV[[i]])
  names(res) <- paste0(SubCortLR[i],"TBV",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[5]))
}

for (i in 1:length(SubCortLR)) {
  res <- augment(SCres_Full[[i]])
  names(res) <- paste0(SubCortLR[i],"Full",names(res))
  SC.res <- cbind(SC.res, as.data.frame(res[6]))
}

SCres_age_ls <-SC.res %>% select(contains("age.resid")) %>% names
SCres_TBV_ls <-SC.res %>% select(contains("TBV.resid")) %>% names
SCres_full_ls <-SC.res %>% select(contains("Full.resid")) %>% names

subCort_age  <- lapply(SCres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=SC.res)
})
subCort_TBV  <- lapply(SCres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs + Sex , data=SC.res)
})
subCort_TBVX  <- lapply(SCres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex , data=SC.res)
})
subCort_full  <- lapply(SCres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=SC.res)
})

## SubCort hemi
subCort_hemi  <- lapply(SubCort, function(i){
  lmer(get(i) ~ Age_in_Yrs + Sex*hemi + (1|Subject), data=Vol.hemi)
})

SCmodels <- c("subCort_simpX", "subCort_simp", "subCort_TBV", "subCort_TBVX")

numSC=length(SubCortLR) #set how many corrections
subcort_out <- extract(SCmodels, numSC)
SC_simpX <- subcort_out[[1]]
SC_simp <- subcort_out[[2]]
SC_TBV <- subcort_out[[3]]
SC_TBVX <- subcort_out[[4]]
SC_hemi <- extract_lmer(subCort_hemi) 

names(SC_simpX) <- paste0('simpX_',names(SC_simpX))
names(SC_simp) <- paste0('simp_',names(SC_simp))
names(SC_TBV) <- paste0('TBV_',names(SC_TBV))
names(SC_TBVX) <- paste0('TBVX_',names(SC_TBVX))
names(SC_hemi) <- paste0('hemi_',names(SC_hemi)) 

SCresid_age <- extractT(subCort_age, numSC)
names(SCresid_age) <- paste0('AgeResid_',names(SCresid_age))
SCresid_full <- extractT(subCort_full, numSC)
names(SCresid_full) <- paste0('FullResid_',names(SCresid_full))

## merge and write out
SC_out <- cbind(SC_simpX, SC_simp, SC_TBV, SC_TBVX, SCresid_age, SCresid_full, SC_hemi) 
SC_out <- apply(SC_out,2,as.character)
rownames(SC_out) <- SubCortLR
SCout.file <- paste(outdir, "SC.csv", sep="/")
write.csv(SC_out, file=SCout.file, row.names = T)

```
# Subcortical variance testing
```{r}
# raw model
# Vol.M <- subset(SC.res, Sex == "Male")
# Vol.F <- subset(SC.res, Sex == "Female")

SC.M.res <- subset(SC.res, Sex == "Male") ##SC.res made above includes residuals 
SC.F.res <- subset(SC.res, Sex == "Female")

SubCort_var  <- lapply(SubCortLR, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar <- extract_var(SubCort_var, numSC)

SubCort_var.resAge  <- lapply(SCres_age_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resAge <- extract_var(SubCort_var.resAge, numSC)

SubCort_var.resTBV  <- lapply(SCres_TBV_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resTBV <- extract_var(SubCort_var.resTBV, numSC)

SubCort_var.resfull  <- lapply(SCres_full_ls, function(i){
  var.test(SC.M.res[[i]], SC.F.res[[i]])
})
SCvar.resfull <- extract_var(SubCort_var.resfull, numSC)

# write out
names(SCvar) <- paste0('VR_',names(SCvar))
names(SCvar.resAge) <- paste0('VR_Age_',names(SCvar.resAge))
names(SCvar.resTBV) <- paste0('VR_TBV_',names(SCvar.resTBV))
names(SCvar.resfull) <- paste0('VR_Full_',names(SCvar.resfull))

SC_VR <- cbind(SCvar, SCvar.resAge, SCvar.resTBV, SCvar.resfull)
SC_VR <- apply(SC_VR,2,as.character)
rownames(SC_VR) <- SubCortLR
SCoutVR.file <- paste(outdir, "SC_VR.csv", sep="/")
write.csv(SC_VR, file=SCoutVR.file, row.names = T)

```

# Subcortical Plots - raw (for age plots) and minus age (box and vio)
```{r}
# make df with hemi and residual data
SC.R.res <- SC.res %>% select(starts_with("R_")) %>% cbind(SC.res[1])
colnames(SC.R.res) <- sub("R_", "", colnames(SC.R.res)) 
SC.R.res$hemi <- "right" 

SC.L.res <- SC.res %>% select(starts_with("L_")) %>% cbind(SC.res[1])
colnames(SC.L.res) <- sub("L_", "", colnames(SC.L.res)) 
SC.L.res$hemi <- "left" 

SC.hemi.res <- rbind(SC.R.res, SC.L.res)
SC.hemi.res <- merge(SC.hemi.res, demogs, by=("Subject")) 

#make lists of regions based on residuals
SC_to_graph_full <-SC.hemi.res %>% select(contains("Full.resid")) %>% names
SC_to_graph_TBV <-SC.hemi.res %>% select(contains("TBV.resid")) %>% names
SC_to_graph_age <-SC.hemi.res %>% select(contains("age.resid")) %>% names

#plot 
SCplots_age <- plot_age_hemi(SubCort, Vol.hemi)
SCplots_box <- plot_box_hemi(SC_to_graph_age, SC.hemi.res)
SCplots_vio <- plot_vio_hemi(SC_to_graph_age, SC.hemi.res)

# check what they look like
plot_grid(plotlist=SCplots_box, align="hv", ncol =3)
plot_grid(plotlist=SCplots_age, align="hv", ncol =2)
plot_grid(plotlist=SCplots_vio, align="hv", ncol =3)

# set arrangement
SC1 <- plot_grid(plotlist=SCplots_box, align="hv", ncol =3)
SC2 <- plot_grid(plotlist=SCplots_age, align="hv", ncol =2)
SC3 <- plot_grid(plotlist=SCplots_vio, align="hv", ncol =3)

#set file names
SCfile.box <- paste(outdir, "SCgraphBox.png", sep="/")
SCfile.age <- paste(outdir, "SCgraphAge.png", sep="/")
SCfile.vio <- paste(outdir, "SCgraphVio.png", sep="/")

#save graphs
ggsave(SCfile.box, SC1, dpi=300, width = 21, height = 17.82, units = "cm")
ggsave(SCfile.age, SC2, dpi=300, width = 21, height = 24, units = "cm")
ggsave(SCfile.vio, SC3, dpi=300, width = 21, height = 17.82, units = "cm")

```
# Subcortical Plots - minus TBV (age plots), minus age and TBV (vio)
```{r}
#plot 
SCplots_age.res <- plot_age_hemi(SC_to_graph_TBV, SC.hemi.res)
SCplots_vio.res <- plot_vio_hemi(SC_to_graph_full, SC.hemi.res)

#check config
plot_grid(plotlist=SCplots_age.res, align="hv", ncol = 3)
plot_grid(plotlist=SCplots_vio.res, align="hv", ncol = 3)

#set config
SC2.res <- plot_grid(plotlist=SCplots_age.res, align="hv", ncol =2)
SC3.res <- plot_grid(plotlist=SCplots_vio.res, align="hv", ncol =3)

#set file names
SCfile.age.res <- paste(outdir, "SCgraphAgeRES.png", sep="/")
SCfile.vio.res <- paste(outdir, "SCgraphVioRES.png", sep="/")

#save
ggsave(SCfile.age.res, SC2.res, dpi=300, width = 21, height = 24, units = "cm")
ggsave(SCfile.vio.res, SC3.res, dpi=300, width = 21, height = 17.82, units = "cm")


#alt config combining with and without TBV
AltSC1 <- plot_grid((SCplots_vio[[1]] + ylab("Thalamus")), (SCplots_vio.res[[1]]+ ylab("Thalamus")), 
                    (SCplots_vio[[2]] +ylab("Caudate")), (SCplots_vio.res[[2]] +ylab("Caudate")), 
                    (SCplots_vio[[3]] +ylab("Putamen")), (SCplots_vio.res[[3]] +ylab("Putamen")),
                    (SCplots_vio[[4]] +ylab("Pallidum")), (SCplots_vio.res[[4]] +ylab("Pallidum")),
                    (SCplots_vio[[5]] +ylab("Hippocampus")), (SCplots_vio.res[[5]] +ylab("Hippocampus")),
                    (SCplots_vio[[6]] +ylab("Amygdala")), (SCplots_vio.res[[6]] +ylab("Amygdala")),
                    (SCplots_vio[[7]] +ylab("Nucleus Accumbens")), (SCplots_vio.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =2)

AltSC3 <- plot_grid((SCplots_vio[[1]] + ylab("Thalamus")),  (SCplots_vio[[2]] +ylab("Caudate")),
                     (SCplots_vio[[3]] +ylab("Putamen")),  (SCplots_vio[[4]] +ylab("Pallidum")),
                    (SCplots_vio[[5]] +ylab("Hippocampus")),(SCplots_vio[[6]] +ylab("Amygdala")), 
                    (SCplots_vio[[7]] +ylab("Nucleus Accumbens")),(SCplots_vio.res[[1]]+ ylab("Thalamus")), 
                    (SCplots_vio.res[[2]] +ylab("Caudate")), (SCplots_vio.res[[3]] +ylab("Putamen")),
                    (SCplots_vio.res[[4]] +ylab("Pallidum")), (SCplots_vio.res[[5]] +ylab("Hippocampus")),
                    (SCplots_vio.res[[6]] +ylab("Amygdala")), (SCplots_vio.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =7)


AltSC2 <- plot_grid((SCplots_age[[1]] +ylab("Thalamus")), (SCplots_age.res[[1]] + ylab("Thalamus")),
                    (SCplots_age[[2]] +ylab("Caudate")), (SCplots_age.res[[2]] +ylab("Caudate")), 
                    (SCplots_age[[3]] +ylab("Putamen")), (SCplots_age.res[[3]] +ylab("Putamen")),
                    (SCplots_age[[4]] +ylab("Pallidum")), (SCplots_age.res[[4]] +ylab("Pallidum")), 
                    (SCplots_age[[5]] +ylab("Hippocampus")), (SCplots_age.res[[5]] +ylab("Hippocampus")), 
                    (SCplots_age[[6]] +ylab("Amygdala")), (SCplots_age.res[[6]] +ylab("Amygdala")),
                    (SCplots_age[[7]] +ylab("Nucleus Accumbens")), (SCplots_age.res[[7]] +ylab("Nucleus Accumbens")), align="hv", ncol =2)

SCfile.alt1 <- paste(outdir, "SCgraphVio_comb.png", sep="/")
SCfile.alt2 <- paste(outdir, "SCgraphAge_comb.png", sep="/")
SCfile.alt3 <- paste(outdir, "SCgraphVio_comb2.png", sep="/")

ggsave(SCfile.alt1, AltSC1, dpi=300, width = 16, height = 29.7, units = "cm")
ggsave(SCfile.alt2, AltSC2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SCfile.alt3, AltSC3, dpi=300, width = 29.7, height = 8, units = "cm")

### just to get a legend
# leg <- ggplot(Vol.hemi.res, aes(x= hemi, fill = Sex, y= ThalamusProperFull.resid)) + geom_split_violin() 
# leg.file <- paste(outdir, "legend.png", sep="/") 
# ggsave(leg.file, leg, dpi=300, width = 16, height = 16, units = "cm")

```
# top/bottom subs SC
```{r}
##Q1 is smallest Q20 largest
#SCres_full_ls list to use

# SC_Qs <- mutate_at(SC.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SC_QsM <- mutate_at(SC.M.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SC_QsF <- mutate_at(SC.F.res, SCres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# SC_Qs <- SC_Qs %>% select(ends_with("_Q")) %>% cbind(SC_Qs[1]) 
# SC_QsM <- SC_QsM %>% select(ends_with("_Q")) %>% cbind(SC_QsM[1]) 
# SC_QsF <- SC_QsF %>% select(ends_with("_Q")) %>% cbind(SC_QsF[1]) 
# 

```

# subcortical atlas plot 
```{r}
areaSC <- c("Thalamus Proper", "Caudate", "Putamen", "Pallidum", "Hippocampus", "Amygdala", "Accumbens")
leftSC <- cbind(areaSC, "left")
rightSC <- cbind(areaSC, "right")
hemisSC <- rbind(leftSC, rightSC) 
colnames(hemisSC) <- c("area", "hemi")

###### for VR
SCplotVR <- as.data.frame(SC_VR, stringsAsFactors = F) %>% cbind(hemisSC)

#select sig
SCplotVR_sig.raw <- subset(SCplotVR, as.numeric(VR_Age_padj_VR) < 0.05)
SCplotVR_sig.cor <- subset(SCplotVR, as.numeric(VR_Full_padj_VR) < 0.05)

#plot
SCa <- ggseg(SCplotVR_sig.raw, atlas="aseg", mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
                        guides(fill=guide_colorbar(title="VR", 
                        title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

SCb <- ggseg(SCplotVR_sig.cor, atlas="aseg", mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SCa, SCb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SC_VR_plot <- plot_grid(SCa, SCb, align="hv", ncol = 1, labels=c('A', 'B'), label_size=10)

#names and save
SC_VR_plot.file <- paste(outdir, "SCatlasVR.png", sep="/")
ggsave(SC_VR_plot.file, SC_VR_plot, dpi=300, width = 21, height = 12, units = "cm")

##mean
SCplot <- as.data.frame(SC_out, stringsAsFactors = F) %>% cbind(hemisSC)
#select sig
SCplot_sig.raw <- subset(SCplot, as.numeric(AgeResid_Padj) < 0.05)
SCplot_sig.cor <- subset(SCplot, as.numeric(FullResid_Padj) < 0.05)

#plot
SCc <- ggseg(SCplot_sig.raw, atlas="aseg", mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                       breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="Cohen's d", title.position = "top", label.theme = element_text(angle = 90, size= 8)))

SCd <- ggseg(SCplot_sig.cor, atlas="aseg", mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                       breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8)))

#arrange
plot_grid(SCc, SCd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SC_plot <- plot_grid(SCc, SCd, align="hv", ncol = 1, labels=c('A', 'B'), label_size=10)

#names and save
SC_plot.file <- paste(outdir, "SCatlas.png", sep="/")
ggsave(SC_plot.file, SC_plot, dpi=300, width = 21, height = 12, units = "cm")

```
# stats cortical CT means
```{r}

## CT simple with interactions
CortCT_simpX  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex, data=CT.df)
})

## Cort simple
CortCT_simp  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs +Sex, data=CT.df)
})

### make df including residuals from TBV 
CT.res <- CT.df
CTres_age  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs, data=CT.res)
})
CTres_TBV  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=CT.res)
})
CTres_Full  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age_in_Yrs, data=CT.res)
})

for (i in 1:length(CortLR)) {
  res <- augment(CTres_age[[i]])
  names(res) <- paste0(CortLR[i],"age",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(CTres_TBV[[i]])
  names(res) <- paste0(CortLR[i],"TBV",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(CTres_Full[[i]])
  names(res) <- paste0(CortLR[i],"Full",names(res))
  CT.res <- cbind(CT.res, as.data.frame(res[6]))
}

CTres_age_ls <-CT.res %>% select(contains("age.resid")) %>% names
CTres_TBV_ls <-CT.res %>% select(contains("TBV.resid")) %>% names
CTres_full_ls <-CT.res %>% select(contains("Full.resid")) %>% names

CT_age  <- lapply(CTres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=CT.res)
})
CortCT_TBV  <- lapply(CTres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs + Sex , data=CT.res)
})
CortCT_TBVX  <- lapply(CTres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex , data=CT.res)
})
CT_full  <- lapply(CTres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=CT.res)
})

## CT hemi
CortCT_hemi  <- lapply(Cort, function(i){
  lmer(get(i) ~ Age_in_Yrs + Sex*hemi + (1|Subject), data=CT.hemi)
})

CTmodels <- c("CortCT_simpX", "CortCT_simp", "CortCT_TBV", "CortCT_TBVX")

numCT=length(CortLR) #set how many corrections
CT_out <- extract(CTmodels, numCT)
CT_simpX <- CT_out[[1]]
CT_simp <- CT_out[[2]]
CT_TBV <- CT_out[[3]]
CT_TBVX <- CT_out[[4]]
CT_hemi <- extract_lmer(CortCT_hemi) 

names(CT_simpX) <- paste0('simpX_',names(CT_simpX))
names(CT_simp) <- paste0('simp_',names(CT_simp))
names(CT_TBV) <- paste0('TBV_',names(CT_TBV))
names(CT_TBVX) <- paste0('TBVX_',names(CT_TBVX))
names(CT_hemi) <- paste0('hemi_',names(CT_hemi)) 

CTresid_age <- extractT(CT_age, numCT)
names(CTresid_age) <- paste0('AgeResid_',names(CTresid_age))
CTresid_full <- extractT(CT_full, numCT)
names(CTresid_full) <- paste0('FullResid_',names(CTresid_full))

## merge and write out
CT_out_tbl <- cbind(CT_simpX, CT_simp, CT_TBV, CT_TBVX, CTresid_age, CTresid_full, CT_hemi) 
CT_out_tbl <- apply(CT_out_tbl,2,as.character)
rownames(CT_out_tbl) <- CortLR
CTout.file <- paste(outdir, "CT.csv", sep="/")
write.csv(CT_out_tbl, file=CTout.file, row.names = T)

```
#  stats cortical CT variance
```{r}
CT.M <- subset(CT.df, Sex == "Male") # 
CT.F <- subset(CT.df, Sex == "Female")

CTCort_var  <- lapply(CortLR, function(i){
  var.test(CT.M[[i]], CT.F[[i]])
})
CTvar <- extract_var(CTCort_var, numCT)

CT.M.res <- subset(CT.res, Sex == "Male") # 
CT.F.res <- subset(CT.res, Sex == "Female")

CTCort_var.resAge  <- lapply(CTres_age_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resAge <- extract_var(CTCort_var.resAge, numCT)

CTCort_var.resTBV  <- lapply(CTres_TBV_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resTBV <- extract_var(CTCort_var.resTBV, numCT)

CTCort_var.resfull  <- lapply(CTres_full_ls, function(i){
  var.test(CT.M.res[[i]], CT.F.res[[i]])
})
CTvar.resfull <- extract_var(CTCort_var.resfull, numCT)

# write out
names(CTvar) <- paste0('VR_',names(CTvar))
names(CTvar.resAge) <- paste0('VR_Age_',names(CTvar.resAge))
names(CTvar.resTBV) <- paste0('VR_TBV_',names(CTvar.resTBV))
names(CTvar.resfull) <- paste0('VR_Full_',names(CTvar.resfull))

CT_VR <- cbind(CTvar, CTvar.resAge, CTvar.resTBV, CTvar.resfull)
CT_VR <- apply(CT_VR,2,as.character)
rownames(CT_VR) <- CortLR
CToutVR.file <- paste(outdir, "CT_VR.csv", sep="/")
write.csv(CT_VR, file=CToutVR.file, row.names = T)

```
# plot CT - raw (for age plots) and minus age (box and vio)
```{r}
#mk df with hemis and resid data
CT.R.res <- CT.res %>% select(starts_with("R_")) %>% cbind(CT.res[1])
colnames(CT.R.res) <- sub("R_", "", colnames(CT.R.res)) 
CT.R.res$hemi <- "right" 

CT.L.res <- CT.res %>% select(starts_with("L_")) %>% cbind(CT.res[1])
colnames(CT.L.res) <- sub("L_", "", colnames(CT.L.res)) 
CT.L.res$hemi <- "left" 

CT.hemi.res <- rbind(CT.R.res, CT.L.res)
CT.hemi.res <- merge(CT.hemi.res, demogs, by=("Subject")) 

#make lists of regions based on residuals
CT_to_graph_age <-CT.hemi.res %>% dplyr::select(contains("age.resid")) %>% names
CT_to_graph_TBV <-CT.hemi.res %>% dplyr::select(contains("TBV.resid")) %>% names
CT_to_graph_full <-CT.hemi.res %>% dplyr::select(contains("Full.resid")) %>% names

#plot
CTplots_box <- plot_box_hemi(CT_to_graph_age, CT.hemi.res)
CTplots_age <- plot_age_hemi(Cort, CT.hemi)
CTplots_vio <- plot_vio_hemi(CT_to_graph_age, CT.hemi.res)

#check arrangement
marrangeGrob(grobs=CTplots_box, ncol =3, nrow =3)
marrangeGrob(grobs=CTplots_age, ncol =2, nrow =2)
marrangeGrob(grobs=CTplots_vio, ncol =3, nrow =3)

#set arranglement
CT1 <- marrangeGrob(grobs=CTplots_box, ncol =3, nrow =5)
CT2 <- marrangeGrob(grobs=CTplots_age, ncol =2, nrow =4)
CT3 <- marrangeGrob(grobs=CTplots_vio, ncol =3, nrow =5)

#set file names
CTfile.box <- paste(outdir, "CTgraphBox.pdf", sep="/")
CTfile.age <- paste(outdir, "CTgraphAge.pdf", sep="/")
CTfile.vio <- paste(outdir, "CTgraphVio.pdf", sep="/")

#save
ggsave(CTfile.box, CT1, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.age, CT2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.vio, CT3, dpi=300, width = 21, height = 29.7, units = "cm")

```
# CT Plots - minus TBV (age plots), minus age and TBV (vio)
```{r}
#plot
CTplots_age.res <- plot_age_hemi(CT_to_graph_TBV, CT.hemi.res)
CTplots_vio.res <- plot_vio_hemi(CT_to_graph_full, CT.hemi.res)

#check arrangment
marrangeGrob(grobs=CTplots_age.res, ncol = 2, nrow =2)
marrangeGrob(grobs=CTplots_vio.res, ncol = 3, nrow =3)

#set arrangment
CT2.res <- marrangeGrob(grobs=CTplots_age.res, ncol =2, nrow =4)
CT3.res <- marrangeGrob(grobs=CTplots_vio.res, ncol =3, nrow =5)

#set file names
CTfile.age.res <- paste(outdir, "CTgraphAgeRES.pdf", sep="/")
CTfile.vio.res <- paste(outdir, "CTgraphVioRES.pdf", sep="/")

#save
ggsave(CTfile.age.res, CT2.res, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(CTfile.vio.res, CT3.res, dpi=300, width = 21, height = 29.7, units = "cm")

```

# top/bottom subs CT
```{r}
##Q1 is smallest Q20 largest
#CTres_full_ls list to use

# CT_Qs <- mutate_at(CT.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# CT_QsM <- mutate_at(CT.M.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# CT_QsF <- mutate_at(CT.F.res, CTres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# CT_Qs <- CT_Qs %>% select(ends_with("_Q")) %>% cbind(CT_Qs[1]) 
# CT_QsM <- CT_QsM %>% select(ends_with("_Q")) %>% cbind(CT_QsM[1]) 
# CT_QsF <- CT_QsF %>% select(ends_with("_Q")) %>% cbind(CT_QsF[1]) 
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))
# 
# colnames(CT_Qs) <- sub("_Q", "_Q_CT", colnames(CT_Qs))
# colnames(CT_QsM) <- sub("_Q", "_Q_CT", colnames(CT_QsM))
# colnames(CT_QsF) <- sub("_Q", "_Q_CT", colnames(CT_QsF))

```
# CT atlas plot 
```{r}
#mk df 
area <- c("banks superior temporal", "caudal anterior cingulate",  "caudal middle frontal", "cuneus", "entorhinal", "fusiform",
                   "inferior parietal", "inferior temporal","isthmus cingulate", "lateraloccipital", "lateralorbito frontal", "lingual",
                   "medial orbito frontal", "middle temporal", "parahippocampal", "para central", "pars opercularis", "pars orbitalis",
                   "pars triangularis", "pericalcarine", "post central", "posterior cingulate", "pre central", "precuneus", 
                   "rostral anterior cingulate", "rostral middle frontal", "superior frontal", "superior parietal", "superior temporal",
                   "supramarginal", "frontal pole", "temporal pole", "transverse temporal", "insula")
left <- cbind(area, "left")
right <- cbind(area, "right")
hemis <- rbind(left, right) 
colnames(hemis) <- c("area", "hemi")

###### for VR
CTplotVR <- as.data.frame(CT_VR, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
CTplotVR_sig.raw <- subset(CTplotVR, as.numeric(VR_Age_padj_VR) < 0.05)
CTplotVR_sig.cor <- subset(CTplotVR, as.numeric(VR_Full_padj_VR) < 0.05)

#plot
CTa <- ggseg(CTplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
    scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 
CTb <- ggseg(CTplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
   scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8)))  

#arrange
plot_grid(CTa, CTb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CT_VR_plot <- plot_grid(CTa, CTb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#names and save
CT_VR_plot.file <- paste(outdir, "CTatlasVR.png", sep="/")
ggsave(CT_VR_plot.file, CT_VR_plot, dpi=300, width = 21, height = 12, units = "cm")

####### for mean
CTplot.df <- as.data.frame(CT_out_tbl, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
CTplot_sig.raw <- subset(CTplot.df, as.numeric(AgeResid_Padj) < 0.05)
CTplot_sig.cor <- subset(CTplot.df, as.numeric(FullResid_Padj) < 0.05)

#plot
CTc <- ggseg(CTplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                       breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8)))  
CTd <- ggseg(CTplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF",mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                       breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTc, CTd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CT_plot <- plot_grid(CTc, CTd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CT_plot.file <- paste(outdir, "CTatlas.png", sep="/")
ggsave(CT_plot.file, CT_plot, dpi=300, width = 21, height = 12, units = "cm")

### for age*sex interaction
## subsets of data that was significant
CTplotX_sig.raw <- subset(CTplot.df, as.numeric(simpX_padj_XTBVheight) < 0.05)
CTplotX_sig.cor <- subset(CTplot.df, as.numeric(TBVX_padj_XTBVheight) < 0.05)
CTplotAGE_sig.raw <- subset(CTplot.df, as.numeric(simp_padj_age) < 0.05)
CTplotAGE_sig.cor <- subset(CTplot.df, as.numeric(TBV_padj_age) < 0.05)

#plot
CTe <- ggseg(CTplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="F", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTf <- ggseg(CTplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTe, CTf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CTX_plot <- plot_grid(CTe, CTf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CTX_plot.file <- paste(outdir, "CTageXsex.png", sep="/")
ggsave(CTX_plot.file, CTX_plot, dpi=300, width = 21, height = 12, units = "cm")

#plot
CTg <- ggseg(CTplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(direction= "horizontal", title="F", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
CTh <- ggseg(CTplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(CTg, CTh, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
CTAGE_plot <- plot_grid(CTg, CTh, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
CTAGE_plot.file <- paste(outdir, "CTatlasAGE.png", sep="/")
ggsave(CTAGE_plot.file, CTAGE_plot, dpi=300, width = 21, height = 12, units = "cm")

```
# stats cortical SA mean
```{r} 
## SA simple with interactions
CortSA_simpX  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex, data=SA.df)
})

## Cort simple
CortSA_simp  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs +Sex, data=SA.df)
})

### make df including residuals from TBV 
SA.res <- SA.df
SAres_age  <- lapply(CortLR, function(i){
  lm(get(i) ~ Age_in_Yrs, data=SA.res)
})
SAres_TBV  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent, data=SA.res)
})
SAres_Full  <- lapply(CortLR, function(i){
  lm(get(i) ~ BrainSeg_No_Vent + Age_in_Yrs, data=SA.res)
})

for (i in 1:length(CortLR)) {
  res <- augment(SAres_age[[i]])
  names(res) <- paste0(CortLR[i],"age",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(SAres_TBV[[i]])
  names(res) <- paste0(CortLR[i],"TBV",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[5]))
}

for (i in 1:length(CortLR)) {
  res <- augment(SAres_Full[[i]])
  names(res) <- paste0(CortLR[i],"Full",names(res))
  SA.res <- cbind(SA.res, as.data.frame(res[6]))
}

SAres_age_ls <-SA.res %>% select(contains("age.resid")) %>% names
SAres_TBV_ls <-SA.res %>% select(contains("TBV.resid")) %>% names
SAres_full_ls <-SA.res %>% select(contains("Full.resid")) %>% names

SA_age  <- lapply(SAres_age_ls, function(i){
  t.test(get(i) ~ Sex , data=SA.res)
})
CortSA_TBV  <- lapply(SAres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs + Sex , data=SA.res)
})
CortSA_TBVX  <- lapply(SAres_TBV_ls, function(i){
  lm(get(i) ~ Age_in_Yrs*Sex , data=SA.res)
})
SA_full  <- lapply(SAres_full_ls, function(i){
  t.test(get(i) ~ Sex , data=SA.res)
})

## SA hemi
CortSA_hemi  <- lapply(Cort, function(i){
  lmer(get(i) ~ Age_in_Yrs + Sex*hemi + (1|Subject), data=SA.hemi)
})

SAmodels <- c("CortSA_simpX", "CortSA_simp", "CortSA_TBV", "CortSA_TBVX")

numSA=length(CortLR) #set how many corrections
SA_out <- extract(SAmodels, numSA)
SA_simpX <- SA_out[[1]]
SA_simp <- SA_out[[2]]
SA_TBV <- SA_out[[3]]
SA_TBVX <- SA_out[[4]]
SA_hemi <- extract_lmer(CortSA_hemi) 

names(SA_simpX) <- paste0('simpX_',names(SA_simpX))
names(SA_simp) <- paste0('simp_',names(SA_simp))
names(SA_TBV) <- paste0('TBV_',names(SA_TBV))
names(SA_TBVX) <- paste0('TBVX_',names(SA_TBVX))
names(SA_hemi) <- paste0('hemi_',names(SA_hemi)) 

SAresid_age <- extractT(SA_age, numSA)
names(SAresid_age) <- paste0('AgeResid_',names(SAresid_age))
SAresid_full <- extractT(SA_full, numSA)
names(SAresid_full) <- paste0('FullResid_',names(SAresid_full))

## merge and write out
SA_out_tbl <- cbind(SA_simpX, SA_simp, SA_TBV, SA_TBVX, SAresid_age, SAresid_full, SA_hemi) 
SA_out_tbl <- apply(SA_out_tbl,2,as.character)
rownames(SA_out_tbl) <- CortLR
SAout.file <- paste(outdir, "SA.csv", sep="/")
write.csv(SA_out_tbl, file=SAout.file, row.names = T)

```
# SA variance testing
```{r}
SA.M <- subset(SA.df, Sex == "Male") # 
SA.F <- subset(SA.df, Sex == "Female")

SACort_var  <- lapply(CortLR, function(i){
  var.test(SA.M[[i]], SA.F[[i]])
})
SAvar <- extract_var(SACort_var, numSA)

SA.M.res <- subset(SA.res, Sex == "Male") # 
SA.F.res <- subset(SA.res, Sex == "Female")

SACort_var.resAge  <- lapply(SAres_age_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resAge <- extract_var(SACort_var.resAge, numSA)

SACort_var.resTBV  <- lapply(SAres_TBV_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resTBV <- extract_var(SACort_var.resTBV, numSA)

SACort_var.resfull  <- lapply(SAres_full_ls, function(i){
  var.test(SA.M.res[[i]], SA.F.res[[i]])
})
SAvar.resfull <- extract_var(SACort_var.resfull, numSA)

# write out
names(SAvar) <- paste0('VR_',names(SAvar))
names(SAvar.resAge) <- paste0('VR_Age_',names(SAvar.resAge))
names(SAvar.resTBV) <- paste0('VR_TBV_',names(SAvar.resTBV))
names(SAvar.resfull) <- paste0('VR_Full_',names(SAvar.resfull))

SA_VR <- cbind(SAvar, SAvar.resAge, SAvar.resTBV, SAvar.resfull)
SA_VR <- apply(SA_VR,2,as.character)
rownames(SA_VR) <- CortLR
SAoutVR.file <- paste(outdir, "SA_VR.csv", sep="/")
write.csv(SA_VR, file=SAoutVR.file, row.names = T)

```
# plot SA - raw (for age plots) and minus age (box and vio)
```{r}
#mk df with hemis and resids
SA.R.res <- SA.res %>% select(starts_with("R_")) %>% cbind(SA.res[1])
colnames(SA.R.res) <- sub("R_", "", colnames(SA.R.res)) 
SA.R.res$hemi <- "right" 

SA.L.res <- SA.res %>% select(starts_with("L_")) %>% cbind(SA.res[1])
colnames(SA.L.res) <- sub("L_", "", colnames(SA.L.res)) 
SA.L.res$hemi <- "left" 

SA.hemi.res <- rbind(SA.R.res, SA.L.res)
SA.hemi.res <- merge(SA.hemi.res, demogs, by=("Subject")) 

#make lits of variable names to graph based of resids
SA_to_graph_age <-SA.hemi.res %>% dplyr::select(contains("age.resid")) %>% names
SA_to_graph_TBV <-SA.hemi.res %>% dplyr::select(contains("TBV.resid")) %>% names
SA_to_graph_full <-SA.hemi.res %>% dplyr::select(contains("Full.resid")) %>% names

#plot
SAplots_box <- plot_box_hemi(SA_to_graph_age, SA.hemi.res)
SAplots_age <- plot_age_hemi(Cort, SA.hemi)
SAplots_vio <- plot_vio_hemi(SA_to_graph_age, SA.hemi.res)

#check arrangement
marrangeGrob(grobs=SAplots_box, ncol =3, nrow =3)
marrangeGrob(grobs=SAplots_age, ncol =2, nrow =2)
marrangeGrob(grobs=SAplots_vio, ncol =3, nrow =3)

#set arrangement
SA1 <- marrangeGrob(grobs=SAplots_box, ncol =3, nrow =5)
SA2 <- marrangeGrob(grobs=SAplots_age, ncol =2, nrow =4)
SA3 <- marrangeGrob(grobs=SAplots_vio, ncol =3, nrow =5)

#set file names
SAfile.box <- paste(outdir, "SAgraphBox.pdf", sep="/")
SAfile.age <- paste(outdir, "SAgraphAge.pdf", sep="/")
SAfile.vio <- paste(outdir, "SAgraphVio.pdf", sep="/")

#save
ggsave(SAfile.box, SA1, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.age, SA2, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.vio, SA3, dpi=300, width = 21, height = 29.7, units = "cm")

```

# SA Plots - minus TBV (age plots), minus age and TBV (vio)
```{r}
#plot
SAplots_age.res <- plot_age_hemi(SA_to_graph_TBV, SA.hemi.res)
SAplots_vio.res <- plot_vio_hemi(SA_to_graph_full, SA.hemi.res)

#arrange
marrangeGrob(grobs=SAplots_age.res, ncol = 2, nrow =2)
marrangeGrob(grobs=SAplots_vio.res, ncol = 3, nrow =3)

#set arrangement
SA2.res <- marrangeGrob(grobs=SAplots_age.res, ncol =2, nrow =4)
SA3.res <- marrangeGrob(grobs=SAplots_vio.res, ncol =3, nrow =5)

#set file names
SAfile.age.res <- paste(outdir, "SAgraphAgeRES.pdf", sep="/")
SAfile.vio.res <- paste(outdir, "SAgraphVioRES.pdf", sep="/")

#save
ggsave(SAfile.age.res, SA2.res, dpi=300, width = 21, height = 29.7, units = "cm")
ggsave(SAfile.vio.res, SA3.res, dpi=300, width = 21, height = 29.7, units = "cm")

```
# top/bottom subs SA
```{r}
##Q1 is smallest Q20 largest
#SAres_full_ls list to use

# SA_Qs <- mutate_at(SA.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SA_QsM <- mutate_at(SA.M.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# SA_QsF <- mutate_at(SA.F.res, SAres_full_ls, funs(Q=as.integer(cut(. , quantile(. , probs=0:20/20), include.lowest=TRUE))))
# 
# SA_Qs <- SA_Qs %>% select(ends_with("_Q")) %>% cbind(SA_Qs[1]) 
# SA_QsM <- SA_QsM %>% select(ends_with("_Q")) %>% cbind(SA_QsM[1]) 
# SA_QsF <- SA_QsF %>% select(ends_with("_Q")) %>% cbind(SA_QsF[1]) 
# 
# colnames(SA_Qs) <- sub("_Q", "_Q_SA", colnames(SA_Qs))
# colnames(SA_QsM) <- sub("_Q", "_Q_SA", colnames(SA_QsM))
# colnames(SA_QsF) <- sub("_Q", "_Q_SA", colnames(SA_QsF))
# 
# ## merge quantile scores from each modality
# Qovsc <- merge(OV_Qs, SC_Qs, by="Subject")
# QovscM <- merge(OV_QsM, SC_QsM, by="Subject")
# QovscF <- merge(OV_QsF, SC_QsF, by="Subject")
# Qcort <- merge(CT_Qs, SA_Qs, by="Subject")
# QcortM <- merge(CT_QsM, SA_QsM, by="Subject")
# QcortF <- merge(CT_QsF, SA_QsF, by="Subject")
# HCP_Qs <- merge(Qovsc, Qcort, by="Subject")
# HCP_QsM <- merge(QovscM, QcortM, by="Subject")
# HCP_QsF <- merge(QovscF, QcortF, by="Subject")
# 
# #make lowest quant=-1 and highest =1. everything else = 0. Sum 
# HCP_Qs_bin <- HCP_Qs 
# HCP_Qs_bin[HCP_Qs_bin == 1] <- -1
# HCP_Qs_bin[HCP_Qs_bin == 20] <- 1
# HCP_Qs_bin[HCP_Qs_bin > 1 & HCP_Qs_bin < 20] <- 0
# HCP_Qs_bin$sum <- rowSums(HCP_Qs_bin[,c(2:156)], na.rm=TRUE)
# 
# HCP_Qs_binM <- HCP_QsM 
# HCP_Qs_binM[HCP_Qs_binM == 1] <- -1
# HCP_Qs_binM[HCP_Qs_binM == 20] <- 1
# HCP_Qs_binM[HCP_Qs_binM > 1 & HCP_Qs_binM < 20] <- 0
# HCP_Qs_binM$sum <- rowSums(HCP_Qs_binM[,c(2:156)], na.rm=TRUE)
# 
# HCP_Qs_binF <- HCP_QsF 
# HCP_Qs_binF[HCP_Qs_binF == 1] <- -1
# HCP_Qs_binF[HCP_Qs_binF == 20] <- 1
# HCP_Qs_binF[HCP_Qs_binF > 1 & HCP_Qs_binF < 20] <- 0
# HCP_Qs_binF$sum <- rowSums(HCP_Qs_binF[,c(2:156)], na.rm=TRUE)
# 
# #melt to long form 
# HCP_Qlong <-melt(HCP_Qs_bin, id.vars=c("Subject", "sum"))
# HCP_QlongM <-melt(HCP_Qs_binM, id.vars=c("Subject", "sum"))
# HCP_QlongF <-melt(HCP_Qs_binF, id.vars=c("Subject", "sum"))
# 
# # ### filter to only keep highest and lowest?
# # HCP_Qlong$filt[HCP_Qlong$value == 1] <- "-1"
# # HCP_Qlong$filt[HCP_Qlong$value == 20] <- "1"
# # HCP_QlongM$filt[HCP_QlongM$value == 1] <- "-1"
# # HCP_QlongM$filt[HCP_QlongM$value == 20] <- "1"
# # HCP_QlongF$filt[HCP_QlongF$value == 1] <- "-1"
# # HCP_QlongF$filt[HCP_QlongF$value == 20] <- "1"
# 
# ##re-order data
# HCP_Qlong <- HCP_Qlong[order(HCP_Qlong$sum),]
# HCP_QlongM <- HCP_QlongM[order(HCP_QlongM$value, HCP_QlongM$variable),]
# HCP_QlongF <- HCP_QlongF[order(HCP_QlongF$value, HCP_QlongF$variable),]
# 
# 
# 
# #### fix colours and order
# ggplot(HCP_Qlong, aes(x=as.factor(Subject), y=variable, fill=sum)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# M1 <- ggplot(HCP_QlongM, aes(x=as.factor(Subject), y=variable, fill=filt)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# M2 <- ggplot(HCP_QlongF, aes(x=as.factor(Subject), y=variable, fill=filt)) + geom_tile() +scale_fill_manual(values = c("yellow","red")) +
#   theme(axis.text=element_blank()) +xlab("Subject") +ylab("region") 
# 
# plot_grid(M1, M2, align="hv", ncol = 2, labels=c('A', 'B'), label_size=10)
# plt <- plot_grid(M1, M2, align="hv", ncol = 2, labels=c('A', 'B'),label_size=10)
# 
# #name and save
# CTX_plot.file <- paste(outdir, "CTageXsex.png", sep="/")
# ggsave(CTX_plot.file, CTX_plot, dpi=300, width = 21, height = 12, units = "cm")



```

# SA atlas plot 
```{r}
area <- c("banks superior temporal", "caudal anterior cingulate",  "caudal middle frontal", "cuneus", "entorhinal", "fusiform",
                   "inferior parietal", "inferior temporal","isthmus cingulate", "lateraloccipital", "lateralorbito frontal", "lingual",
                   "medial orbito frontal", "middle temporal", "parahippocampal", "para central", "pars opercularis", "pars orbitalis",
                   "pars triangularis", "pericalcarine", "post central", "posterior cingulate", "pre central", "precuneus", 
                   "rostral anterior cingulate", "rostral middle frontal", "superior frontal", "superior parietal", "superior temporal",
                   "supramarginal", "frontal pole", "temporal pole", "transverse temporal", "insula")

left <- cbind(area, "left")
right <- cbind(area, "right")
hemis <- rbind(left, right) 
colnames(hemis) <- c("area", "hemi")

SAplotVR <- as.data.frame(SA_VR, stringsAsFactors = F) %>% cbind(hemis)

## select subset of sig data
SAplotVR_sig.raw <- subset(SAplotVR, as.numeric(VR_Age_padj_VR) < 0.05)
SAplotVR_sig.cor <- subset(SAplotVR, as.numeric(VR_Full_padj_VR) < 0.05)

#plot
SAa <- ggseg(SAplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
    scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8)))  
SAb <- ggseg(SAplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
    scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), 
                       breaks=seq(1,2.81,by=0.5)) + theme(axis.title.x = element_blank()) +
  guides(fill=guide_colorbar(title="VR", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAa,SAb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_VR_plot <- plot_grid(SAa,SAb, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#names and save
SA_VR_plot.file <- paste(outdir, "SAatlasVR.png", sep="/")
ggsave(SA_VR_plot.file, SA_VR_plot, dpi=300, width = 21, height = 12, units = "cm")

####### for mean
SAplot.df <- as.data.frame(SA_out_tbl, stringsAsFactors = F) %>% cbind(hemis)

## subsets of data that was significant
SAplot_sig.raw <- subset(SAplot.df, as.numeric(AgeResid_Padj) < 0.05)
SAplot_sig.cor <- subset(SAplot.df, as.numeric(FullResid_Padj) < 0.05)

#plot
SAc <- ggseg(SAplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                      breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
    guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8)))  
SAd <- ggseg(SAplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), 
                      breaks=seq(-1,1,by=1)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="Cohen's d", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAc, SAd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_plot <- plot_grid(SAc, SAd, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
SA_plot.file <- paste(outdir, "SAatlas.png", sep="/")
ggsave(SA_plot.file, SA_plot, dpi=300, width = 21, height = 12, units = "cm")


######### for age
## subsets of data that was significant
SAplotAGE_sig.raw <- subset(SAplot.df, as.numeric(simp_padj_age) < 0.05)
SAplotAGE_sig.cor <- subset(SAplot.df, as.numeric(TBV_padj_age) < 0.05)
SAplotX_sig.raw <- subset(SAplot.df, as.numeric(simpX_padj_XTBVheight) < 0.05)
SAplotX_sig.cor <- subset(SAplot.df, as.numeric(TBVX_padj_XTBVheight) < 0.05)

#plot
SAe <- ggseg(SAplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(axis.title.x = element_blank())+ 
  guides(fill=guide_colorbar(title="F", direction = "horizontal", title.position = "top", label.theme = element_text(angle = 90, size= 8))) 
SAf <- ggseg(SAplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(axis.title.x = element_blank()) + 
  guides(fill=guide_colorbar(title="F", title.position = "left", label.theme = element_text(angle = 0, size= 8))) 

#arrange
plot_grid(SAe, SAf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)
SA_plotAGE <- plot_grid(SAe, SAf, align="hv", ncol = 1, labels=c('A', 'B'),label_size=10)

#name and save
SA_plotAGE.file <- paste(outdir, "SAatlasAGE.png", sep="/")
ggsave(SA_plotAGE.file, SA_plotAGE, dpi=300, width = 21, height = 12, units = "cm")

```

# unit sphere stuff
```{r}
colnames(CT.res) <- paste0("CT_", colnames(CT.res))
colnames(SA.res) <- paste0("SA_", colnames(SA.res))

All.res <- merge(Vol.res, SC.res, by="Subject") %>% merge(CT.res, by.x="Subject", by.y="CT_Subject") %>% 
  merge(SA.res, by.x="Subject", by.y="SA_Subject") %>% 
  select(contains("Full.resid")) %>% cbind(Vol.res[c("Subject", "Age_in_Yrs", "Sex")]) 

Allres.file <- paste(outdir, "Allres.csv", sep="/")
write.csv(All.res, file=Allres.file, row.names = T)

```

# Prep HCP graphs for combining with PNC # need to run FreeSurferPNC.Rmd to have PNC graphs avail
```{r}

#plot required HCP graphs without legends (the same is done for PNC at the end of that script)

##SC
HCP_SCraw <- ggseg(SCplot_sig.raw, atlas="aseg",mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())
HCP_SCcor <- ggseg(SCplot_sig.cor, atlas="aseg", mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())

HCP_SCrawVR <- ggseg(SCplotVR_sig.raw, atlas="aseg", mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
    scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5))  + 
  theme(legend.position="none", axis.title.x = element_blank())
HCP_SCcorVR <- ggseg(SCplotVR_sig.cor, atlas="aseg", mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5))  + 
  theme(legend.position="none", axis.title.x = element_blank())

##CT
HCP_CTraw <- ggseg(CTplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())
HCP_CTcor <- ggseg(CTplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())

HCP_CTrawVR <- ggseg(CTplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
    scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5))  + 
  theme(legend.position="none", axis.title.x = element_blank())
HCP_CTcorVR <- ggseg(CTplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5))  + 
  theme(legend.position="none", axis.title.x = element_blank())

HCP_CTrawAGExSEX <- ggseg(CTplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(legend.position="none", axis.title.x = element_blank()) 
HCP_CTcorAGExSEX <- ggseg(CTplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 30), breaks=seq(0,30,by=15)) + theme(legend.position="none", axis.title.x = element_blank()) 

HCP_CTrawAGE <- ggseg(CTplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(legend.position="none", axis.title.x = element_blank()) 
HCP_CTcorAGE <- ggseg(CTplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 600), breaks=seq(0,600,by=100)) + theme(legend.position="none", axis.title.x = element_blank()) 

##SA
HCP_SAraw <- ggseg(SAplot_sig.raw, mapping=aes(fill=as.numeric(AgeResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())
HCP_SAcor <- ggseg(SAplot_sig.cor, mapping=aes(fill=as.numeric(FullResid_Cohen)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#0033FF", mid="white", high="#FF3300", midpoint=0, limits=c(-1.4, 1.4), breaks=seq(-1,1,by=1)) + 
  theme(legend.position="none", axis.title.x = element_blank())

HCP_SArawVR <- ggseg(SAplotVR_sig.raw, mapping=aes(fill=as.numeric(VR_Age_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5)) +
  theme(legend.position="none", axis.title.x = element_blank())
HCP_SAcorVR <- ggseg(SAplotVR_sig.cor, mapping=aes(fill=as.numeric(VR_Full_VR)), colour="black", size=0.4) +
  scale_fill_gradient2(low="#006600", mid="#FFFF99", high="#FF9900", midpoint=1.8, limits=c(1, 2.81), breaks=seq(1,2.81,by=0.5))  + 
  theme(legend.position="none", axis.title.x = element_blank())
  
HCP_SArawAGE <- ggseg(SAplotAGE_sig.raw, mapping=aes(fill=as.numeric(simp_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(legend.position="none", axis.title.x = element_blank())
HCP_SAcorAGE <- ggseg(SAplotAGE_sig.cor, mapping=aes(fill=as.numeric(TBV_F_age)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 120), breaks=seq(0,120,by=30)) + theme(legend.position="none", axis.title.x = element_blank()) 

HCP_SArawAGExSEX <- ggseg(SAplotX_sig.raw, mapping=aes(fill=as.numeric(simpX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 15), breaks=seq(0,15,by=5)) + theme(legend.position="none", axis.title.x = element_blank())
HCP_SAcorAGExSEX <- ggseg(SAplotX_sig.cor, mapping=aes(fill=as.numeric(TBVX_F_XTBVheight)), colour="black", size=0.4) +
  scale_fill_gradient(limits=c(0, 15), breaks=seq(0,15,by=5)) + theme(legend.position="none", axis.title.x = element_blank()) 


## rename HCP OV & SC
HCP_OVplots_vio <- OVplots_vio
HCP_OVplots_vio.res <- OVplots_vio.res
HCP_OVplots_age <- OVplots_age
HCP_OVplots_age.res <- OVplots_age.res


```
# combine HCP, PNC & OASIS graphs
```{r}
outdir_combined <- "/projects/nforde/HCP/stats/combined_figures"

#arrange
Comb_SC_plot <- plot_grid(PNC_SCraw, HCP_SCraw,  OASIS_SCraw,  PNC_SCcor, HCP_SCcor,  OASIS_SCcor,
                          PNC_SCrawVR, HCP_SCrawVR,  OASIS_SCrawVR,  PNC_SCcorVR, HCP_SCcorVR,  OASIS_SCcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', '','D', 'E', 'F', '','',''), label_size=12)

Comb_SA_plot <- plot_grid(PNC_SAraw, HCP_SAraw,  OASIS_SAraw,  PNC_SAcor, HCP_SAcor,  OASIS_SAcor,
                          PNC_SArawVR, HCP_SArawVR,  OASIS_SArawVR,  PNC_SAcorVR, HCP_SAcorVR,  OASIS_SAcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', '','D', 'E', 'F', '','',''), label_size=12)

Comb_CT_plot <- plot_grid(PNC_CTraw, HCP_CTraw,  OASIS_CTraw,  PNC_CTcor, HCP_CTcor,  OASIS_CTcor,
                          PNC_CTrawVR, HCP_CTrawVR,  OASIS_CTrawVR,  PNC_CTcorVR, HCP_CTcorVR,  OASIS_CTcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', '','D', 'E', 'F', '','',''), label_size=12)

#name and save
Comb_SA_plot.file <- paste(outdir_combined, "HCP_PNC_OASIS_SAatlas.png", sep="/")
Comb_CT_plot.file <- paste(outdir_combined, "HCP_PNC_OASIS_CTatlas.png", sep="/")
Comb_SC_plot.file <- paste(outdir_combined, "HCP_PNC_OASIS_SCatlas.png", sep="/")
ggsave(Comb_SA_plot.file, Comb_SA_plot, dpi=300, width = 21, height = 12, units = "cm")
ggsave(Comb_CT_plot.file, Comb_CT_plot, dpi=300, width = 21, height = 12, units = "cm")
ggsave(Comb_SC_plot.file, Comb_SC_plot, dpi=300, width = 21, height = 12, units = "cm")

##VR only
#arrange
Comb_SC_VR_plot <- plot_grid(PNC_SCrawVR, HCP_SCrawVR,  OASIS_SCrawVR,  PNC_SCcorVR, HCP_SCcorVR,  OASIS_SCcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)

Comb_SA_VR_plot <- plot_grid(PNC_SArawVR, HCP_SArawVR,  OASIS_SArawVR,  PNC_SAcorVR, HCP_SAcorVR,  OASIS_SAcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)

Comb_CT_VR_plot <- plot_grid(PNC_CTrawVR, HCP_CTrawVR,  OASIS_CTrawVR,  PNC_CTcorVR, HCP_CTcorVR,  OASIS_CTcorVR, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)
#name and save
Comb_SC_VR_plot.file <- paste(outdir_combined, "Comb_VR_SCatlas.png", sep="/")
Comb_SA_VR_plot.file <- paste(outdir_combined, "Comb_VR_SAatlas.png", sep="/")
Comb_CT_VR_plot.file <- paste(outdir_combined, "Comb_VR_CTatlas.png", sep="/")
ggsave(Comb_SA_VR_plot.file, Comb_SA_VR_plot, dpi=300, width = 21, height = 10, units = "cm")
ggsave(Comb_CT_VR_plot.file, Comb_CT_VR_plot, dpi=300, width = 21, height = 10, units = "cm")
ggsave(Comb_SC_VR_plot.file, Comb_SC_VR_plot, dpi=300, width = 21, height = 10, units = "cm")

## mean only
Comb_SC_x_plot <- plot_grid(PNC_SCraw, HCP_SCraw,  OASIS_SCraw,  PNC_SCcor, HCP_SCcor,  OASIS_SCcor, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)

Comb_SA_x_plot <- plot_grid(PNC_SAraw, HCP_SAraw,  OASIS_SAraw,  PNC_SAcor, HCP_SAcor,  OASIS_SAcor, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)

Comb_CT_x_plot <- plot_grid(PNC_CTraw, HCP_CTraw,  OASIS_CTraw,  PNC_CTcor, HCP_CTcor,  OASIS_CTcor, align="hv", ncol = 3,
          labels=c('A', 'B', 'C', '','', ''), label_size=12)
#name and save
Comb_SC_x_plot.file <- paste(outdir_combined, "Comb_mean_SCatlas.png", sep="/")
Comb_SA_x_plot.file <- paste(outdir_combined, "Comb_mean_SAatlas.png", sep="/")
Comb_CT_x_plot.file <- paste(outdir_combined, "Comb_mean_CTatlas.png", sep="/")
ggsave(Comb_SA_x_plot.file, Comb_SA_x_plot, dpi=300, width = 21, height = 10, units = "cm")
ggsave(Comb_CT_x_plot.file, Comb_CT_x_plot, dpi=300, width = 21, height = 10, units = "cm")
ggsave(Comb_SC_x_plot.file, Comb_SC_x_plot, dpi=300, width = 21, height = 10, units = "cm")


#global
Comb_OV_Vio <- plot_grid((PNC_OVplots_vio[[1]] + ylab("Total Brain Volume") + ylim(800000, 1600000) + 
                            theme(axis.ticks.x=element_blank())), NULL,
                          (HCP_OVplots_vio[[1]] + ylab("Total Brain Volume") + ylim(800000, 1600000) +
                           theme(axis.ticks.x=element_blank())), NULL ,
                          (OASIS_OVplots_vio[[1]] + ylab("Total Brain Volume") + ylim(800000, 1600000) +
                             theme(axis.ticks.x=element_blank())), NULL,
          (PNC_OVplots_vio[[2]] +ylab("Cerebral Grey Matter") + ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (PNC_OVplots_vio.res[[2]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (HCP_OVplots_vio[[2]] +ylab("Cerebral Grey Matter")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (HCP_OVplots_vio.res[[2]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (OASIS_OVplots_vio[[2]] +ylab("Cerebral Grey Matter")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (OASIS_OVplots_vio.res[[2]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (PNC_OVplots_vio[[3]] +ylab("Cerebral White Matter")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (PNC_OVplots_vio.res[[3]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (HCP_OVplots_vio[[3]] +ylab("Cerebral White Matter")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (HCP_OVplots_vio.res[[3]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (OASIS_OVplots_vio[[3]] +ylab("Cerebral White Matter")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())), (OASIS_OVplots_vio.res[[3]] +ylab("")+ ylim(-200000, 200000) +
                             theme(axis.ticks.x=element_blank())),
          (PNC_OVplots_vio[[4]] +ylab("Cerebellar Grey Matter")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())), (PNC_OVplots_vio.res[[4]] +ylab("")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())),
          (HCP_OVplots_vio[[4]] +ylab("Cerebellar Grey Matter")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())), (HCP_OVplots_vio.res[[4]] +ylab("")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())),
          (OASIS_OVplots_vio[[4]] +ylab("Cerebellar Grey Matter")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())), (OASIS_OVplots_vio.res[[4]] +ylab("")+ ylim(-40000, 40000) +
                             theme(axis.ticks.x=element_blank())),
          (PNC_OVplots_vio[[5]] +ylab("Cerebellar White Matter")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())), (PNC_OVplots_vio.res[[5]] +ylab("")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())),
          (HCP_OVplots_vio[[5]] +ylab("Cerebellar White Matter")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())), (HCP_OVplots_vio.res[[5]] +ylab("")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())),
          (OASIS_OVplots_vio[[5]] +ylab("Cerebellar White Matter")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())), (OASIS_OVplots_vio.res[[5]] +ylab("")+ ylim(-20000, 20000) +
                             theme(axis.ticks.x=element_blank())),
          align="hv", ncol =6)#,
          # labels=c('A','','B','','','','','','','',''), label_size=12)

Comb_OV_Vio.file <- paste(outdir_combined, "HCP_PNC_OASIS_OV_Vio.png", sep="/")
ggsave(Comb_OV_Vio.file, Comb_OV_Vio, dpi=300, width = 30, height = 20, units = "cm")

```